---
title: "Ageing Brain Project"
#author: "Antonino Malacrinò"
date: "`r format(Sys.time(), '%d %B, %Y')`"
output: html_notebook
code_download: true
---
```{r, warning=FALSE, message=FALSE, echo=FALSE}
library("plyr")
library("taRifx")
library("DESeq2")
library("ggplot2")
library("Rmisc")
library("reshape")
library("broom")
library("dplyr")
library("tidyr")
library("data.table")
library("ggpubr")
library("tibble")
library("compare")
library("lme4")
library("car")
library("emmeans")
library("rstanarm")
library("shinystan")
library("brms")
library("cowplot")
library("gdata")
library("cocor")
library("ggpmisc")
library("bayesplot")
library("readr")
dir.create("Figures", showWarnings = FALSE) #this creates a folder for figures, if it does not exist
dir.create("Tables", showWarnings = FALSE)
```

```{r, warning=FALSE, message=FALSE, echo=FALSE}
# Load data
raw.data <- read.table("../data/count_data.txt", sep="\t", header = T, row.names = 1)
raw.data<-raw.data[1:(nrow(raw.data)-7),]
colnames(raw.data) <- sub("_S.*", "", colnames(raw.data))
metadata <- read.table("../data/metadata.txt", sep="\t", header = T)

metadata <- metadata[which(metadata$Population!="Dah_outbred"),]
metadata <- metadata[which(metadata$Age!="A3"),]

metadata.lhm <- metadata[which(metadata$Population=="Lhm"),]
data.lhm <- raw.data[ ,(colnames(raw.data) %in% metadata.lhm$NGI_reference)]
data.lhm <- data.lhm[,apply(data.lhm,2,sum)>=2e6] 
metadata.lhm <- metadata.lhm[metadata.lhm$NGI_reference %in% (colnames(data.lhm)),] 

metadata.dah <- metadata[which(metadata$Population=="Dahomey"),]
data.dah <- raw.data[ ,(colnames(raw.data) %in% metadata.dah$NGI_reference)]
data.dah <- data.dah[,apply(data.dah,2,sum)>=2e6] 
metadata.dah <- metadata.dah[metadata.dah$NGI_reference %in% (colnames(data.dah)),]

ts <- read.table("../data/tissue_specificity.csv", header = T, sep = "\t")

# DESeq model -- LHm
cds <- DESeqDataSetFromMatrix(data.lhm, metadata.lhm, ~ Sex * Age)
cds$group <- factor(paste0(cds$Sex, cds$Age))
design(cds) <- ~ group
dds.lhm <-DESeq(cds,betaPrior=FALSE)
countdata <- estimateSizeFactors(cds)
cdsBlind <- estimateDispersions(countdata)
vstdata.lhm <- varianceStabilizingTransformation(cdsBlind)

# DESeq model -- Dahomey
cds <- DESeqDataSetFromMatrix(data.dah, metadata.dah, ~ Sex * Age)
cds$group <- factor(paste0(cds$Sex, cds$Age))
design(cds) <- ~ group
dds.dah <-DESeq(cds,betaPrior=FALSE)
countdata <- estimateSizeFactors(cds)
cdsBlind <- estimateDispersions(countdata)
vstdata.dah <- varianceStabilizingTransformation(cdsBlind)
```

```{r, warning=FALSE, message=FALSE, echo=FALSE}
#Create working datasets
contrast.calculator <- function(dataset, term1, term2, population){
  dataset$group <- relevel(dataset$group, ref = term2)
  dataset <- nbinomWaldTest(dataset, betaPrior=TRUE)
  set.seed(1)
  res.de <- results(dataset, contrast=c("group", term1, term2))
  res.de <- as.data.frame(res.de)
  res.de <- setDT(res.de, keep.rownames = TRUE)[]
  res.de <- res.de[,c("rn", "log2FoldChange", "padj")]

  colnames(res.de) <- c("Gene", "log2FoldChange", "padj")
  res.de$Population <- paste0(population)
  return(res.de)
}

sb.calculator <- function(dataset, p.threshold, term1, term2, population){
  results.merged <- contrast.calculator(dataset = dataset, term1 = term1, term2 = term2, population = population)
  results.merged$bias <- NA
  results.merged$log2FoldChange <- ifelse(abs(results.merged$log2FoldChange) > 3.5, NA, results.merged$log2FoldChange)
  results.merged$bias <- ifelse(results.merged$log2FoldChange > 0 & results.merged$padj < p.threshold, "Female_biased",
                                ifelse(results.merged$log2FoldChange < 0 & results.merged$padj < p.threshold , "Male_biased",
                                       "Unbiased"))
  colnames(results.merged)[1] <- "Gene"
  results.merged$bias[is.na(results.merged$bias)] <- "Unbiased" #"Undefined" if we want to remove any gene associated with NA
  
  sb.genes <- results.merged[,c("Gene", "log2FoldChange", "bias", "Population")]
  return(sb.genes)
}
```

# Number of SB genes {.tabset}
## Padj <.05
```{r, warning=FALSE, message=FALSE, echo=FALSE}
sb.genes.nr.fun <- function(p.threshold){
  n_genes <- 17558
  sb.genes.lhm.y <- sb.calculator(dataset = dds.lhm, p.threshold = p.threshold, term1 = "FemaleA1", term2 = "MaleA1", population = "LHm")
  sb.genes.lhm.o <- sb.calculator(dataset = dds.lhm, p.threshold = p.threshold, term1 = "FemaleA2", term2 = "MaleA2", population = "LHm")
  sb.genes.dah.y <- sb.calculator(dataset = dds.dah, p.threshold = p.threshold, term1 = "FemaleA1", term2 = "MaleA1", population = "Dahomey")
  sb.genes.dah.o <- sb.calculator(dataset = dds.dah, p.threshold = p.threshold, term1 = "FemaleA2", term2 = "MaleA2", population = "Dahomey")
  sb.genes.y <- rbind(sb.genes.lhm.y, sb.genes.dah.y)
  sb.genes.y$Age <- "Young"
  sb.genes.o <- rbind(sb.genes.lhm.o, sb.genes.dah.o)
  sb.genes.o$Age <- "Old"
  sb.genes <- rbind(sb.genes.y, sb.genes.o)
  sb.genes <- dcast(setDT(sb.genes), Population + bias ~ Age, length)
  sb.genes <- sb.genes %>%
                      rowwise() %>% 
                      mutate(
                        chi.sq = chisq.test(matrix(c(Young, Old, (n_genes - Young), (n_genes - Old)), nrow=2))$statistic,
                        p_val = chisq.test(matrix(c(Young, Old, (n_genes - Young), (n_genes - Old)), nrow=2))$p.value * 4 # Bonferroni, 4 tests
                        )
  sb.genes <- sb.genes[,c("Population", "bias", "Young", "Old", "chi.sq", "p_val")]
return(sb.genes %>% filter(bias != "Unbiased"))
}

sb.genes.nr <- sb.genes.nr.fun(p.threshold = 0.05)
write.table(sb.genes.nr, "Tables/sb_genes_0.05.csv", quote = FALSE, sep = ",", row.names = FALSE)
sb.genes.nr
```

## Padj<.01
```{r, warning=FALSE, message=FALSE, echo=FALSE}
sb.genes.nr <- sb.genes.nr.fun(p.threshold = 0.01)
write.table(sb.genes.nr, "Tables/sb_genes_0.01.csv", quote = FALSE, sep = ",", row.names = FALSE)
sb.genes.nr
```

## Padj<.001
```{r, warning=FALSE, message=FALSE, echo=FALSE}
sb.genes.nr <- sb.genes.nr.fun(p.threshold = 0.001)
write.table(sb.genes.nr, "Tables/sb_genes_0.001.csv", quote = FALSE, sep = ",", row.names = FALSE)
sb.genes.nr
```

## Venn diagram
```{r, warning=FALSE, message=FALSE, echo=FALSE}
p.threshold <- 0.05

sb.genes.lhm.y <- sb.calculator(dataset = dds.lhm, p.threshold = p.threshold, term1 = "FemaleA1", term2 = "MaleA1", population = "LHm")
sb.genes.dah.y <- sb.calculator(dataset = dds.dah, p.threshold = p.threshold, term1 = "FemaleA1", term2 = "MaleA1", population = "Dahomey")
sb.genes.lhm.o <- sb.calculator(dataset = dds.lhm, p.threshold = p.threshold, term1 = "FemaleA2", term2 = "MaleA2", population = "LHm")
sb.genes.dah.o <- sb.calculator(dataset = dds.dah, p.threshold = p.threshold, term1 = "FemaleA2", term2 = "MaleA2", population = "Dahomey")

sb.genes.lhm.y <- sb.genes.lhm.y[!is.na(sb.genes.lhm.y$log2FoldChange),]
sb.genes.dah.y <- sb.genes.dah.y[!is.na(sb.genes.dah.y$log2FoldChange),]
sb.genes.lhm.o <- sb.genes.lhm.o[!is.na(sb.genes.lhm.o$log2FoldChange),]
sb.genes.dah.o <- sb.genes.dah.o[!is.na(sb.genes.dah.o$log2FoldChange),]

male.biased.genes.dah.y <- (sb.genes.dah.y %>% filter(bias == "Male_biased"))$Gene
female.biased.genes.dah.y <- (sb.genes.dah.y %>% filter(bias == "Female_biased"))$Gene
unbiased.genes.dah.y <- (sb.genes.dah.y %>% filter(bias == "Unbiased"))$Gene

male.biased.genes.lhm.y <- (sb.genes.lhm.y %>% filter(bias == "Male_biased"))$Gene
female.biased.genes.lhm.y <- (sb.genes.lhm.y %>% filter(bias == "Female_biased"))$Gene
unbiased.genes.lhm.y <- (sb.genes.lhm.y %>% filter(bias == "Unbiased"))$Gene

male.biased.genes.dah.o <- (sb.genes.dah.o %>% filter(bias == "Male_biased"))$Gene
female.biased.genes.dah.o <- (sb.genes.dah.o %>% filter(bias == "Female_biased"))$Gene
unbiased.genes.dah.o <- (sb.genes.dah.o %>% filter(bias == "Unbiased"))$Gene

male.biased.genes.lhm.o <- (sb.genes.lhm.o %>% filter(bias == "Male_biased"))$Gene
female.biased.genes.lhm.o <- (sb.genes.lhm.o %>% filter(bias == "Female_biased"))$Gene
unbiased.genes.lhm.o <- (sb.genes.lhm.o %>% filter(bias == "Unbiased"))$Gene

df.y <- data.frame(Term1 = c("Dah_FB", "Dah_FB", "Dah_FB", "Dah_FB", " ",  
                           "Dah_MB", "Dah_MB", "Dah_MB", "Dah_MB", " ", 
                           "Dah_UB", "Dah_UB", "Dah_UB", "Dah_UB", " "),
                 Term2 = c("LHm_FB", "LHm_MB", "LHm_UB", " ", "LHm_FB",
                           "LHm_FB", "LHm_MB", "LHm_UB", " ", "LHm_MB",
                           "LHm_FB", "LHm_MB", "LHm_UB", " ", "LHm_UB"),
                 value = c(
                   sum(female.biased.genes.dah.y %in% female.biased.genes.lhm.y),
                   sum(female.biased.genes.dah.y %in% male.biased.genes.lhm.y),
                   sum(female.biased.genes.dah.y %in% unbiased.genes.lhm.y),
                   sum(!(female.biased.genes.dah.y %in% female.biased.genes.lhm.y & female.biased.genes.dah.y %in% male.biased.genes.lhm.y & female.biased.genes.dah.y %in% unbiased.genes.lhm.y)),
                   sum(!(female.biased.genes.lhm.y %in% female.biased.genes.dah.y & female.biased.genes.lhm.y %in% male.biased.genes.dah.y & female.biased.genes.lhm.y %in% unbiased.genes.dah.y)),
                   
                   sum(male.biased.genes.dah.y %in% female.biased.genes.lhm.y),
                   sum(male.biased.genes.dah.y %in% male.biased.genes.lhm.y),
                   sum(male.biased.genes.dah.y %in% unbiased.genes.lhm.y),
                   sum(!(male.biased.genes.dah.y %in% female.biased.genes.lhm.y & male.biased.genes.dah.y %in% male.biased.genes.lhm.y & male.biased.genes.dah.y %in% unbiased.genes.lhm.y)),
                   sum(!(male.biased.genes.lhm.y %in% female.biased.genes.dah.y & male.biased.genes.lhm.y %in% male.biased.genes.dah.y & male.biased.genes.lhm.y %in% unbiased.genes.dah.y)),
                   
                   sum(unbiased.genes.dah.y %in% female.biased.genes.lhm.y),
                   sum(unbiased.genes.dah.y %in% male.biased.genes.lhm.y),
                   sum(unbiased.genes.dah.y %in% unbiased.genes.lhm.y),
                   sum(!(unbiased.genes.dah.y %in% female.biased.genes.lhm.y & unbiased.genes.dah.y %in% male.biased.genes.lhm.y & unbiased.genes.dah.y %in% unbiased.genes.lhm.y)),
                   sum(!(unbiased.genes.lhm.y %in% female.biased.genes.dah.y & unbiased.genes.lhm.y %in% male.biased.genes.dah.y & unbiased.genes.lhm.y %in% unbiased.genes.dah.y))
                 ))

df.o <- data.frame(Term1 = c("Dah_FB", "Dah_FB", "Dah_FB", "Dah_FB", " ",  
                           "Dah_MB", "Dah_MB", "Dah_MB", "Dah_MB", " ", 
                           "Dah_UB", "Dah_UB", "Dah_UB", "Dah_UB", " "),
                 Term2 = c("LHm_FB", "LHm_MB", "LHm_UB", " ", "LHm_FB",
                           "LHm_FB", "LHm_MB", "LHm_UB", " ", "LHm_MB",
                           "LHm_FB", "LHm_MB", "LHm_UB", " ", "LHm_UB"),
                 value = c(
                   sum(female.biased.genes.dah.o %in% female.biased.genes.lhm.o),
                   sum(female.biased.genes.dah.o %in% male.biased.genes.lhm.o),
                   sum(female.biased.genes.dah.o %in% unbiased.genes.lhm.o),
                   sum(!(female.biased.genes.dah.o %in% female.biased.genes.lhm.o & female.biased.genes.dah.o %in% male.biased.genes.lhm.o & female.biased.genes.dah.o %in% unbiased.genes.lhm.o)),
                   sum(!(female.biased.genes.lhm.o %in% female.biased.genes.dah.o & female.biased.genes.lhm.o %in% male.biased.genes.dah.o & female.biased.genes.lhm.o %in% unbiased.genes.dah.o)),
                   
                   sum(male.biased.genes.dah.o %in% female.biased.genes.lhm.o),
                   sum(male.biased.genes.dah.o %in% male.biased.genes.lhm.o),
                   sum(male.biased.genes.dah.o %in% unbiased.genes.lhm.o),
                   sum(!(male.biased.genes.dah.o %in% female.biased.genes.lhm.o & male.biased.genes.dah.o %in% male.biased.genes.lhm.o & male.biased.genes.dah.o %in% unbiased.genes.lhm.o)),
                   sum(!(male.biased.genes.lhm.o %in% female.biased.genes.dah.o & male.biased.genes.lhm.o %in% male.biased.genes.dah.o & male.biased.genes.lhm.o %in% unbiased.genes.dah.o)),
                   
                   sum(unbiased.genes.dah.o %in% female.biased.genes.lhm.o),
                   sum(unbiased.genes.dah.o %in% male.biased.genes.lhm.o),
                   sum(unbiased.genes.dah.o %in% unbiased.genes.lhm.o),
                   sum(!(unbiased.genes.dah.o %in% female.biased.genes.lhm.o & unbiased.genes.dah.o %in% male.biased.genes.lhm.o & unbiased.genes.dah.o %in% unbiased.genes.lhm.o)),
                   sum(!(unbiased.genes.lhm.o %in% female.biased.genes.dah.o & unbiased.genes.lhm.o %in% male.biased.genes.dah.o & unbiased.genes.lhm.o %in% unbiased.genes.dah.o))
                 ))
  
p.y <- ggplot(df.y, aes(Term1, Term2)) +
  theme_bw(base_size = 12) +
  ggtitle("Young flies") +
  geom_tile(aes(fill = value), color='white', size = 0.5) +
  coord_equal() +
  geom_text(aes(Term1, Term2, label = value), color = "black", size = 5)  +
  scale_fill_gradient2(low = "#e0f3db", high = "#e0f3db", mid = "#e0f3db", 
                       midpoint = 0.5, limit = c(0,1000000), space = "Lab") +
  theme(plot.background = element_blank(),
        plot.title = element_text(hjust = 0.5),
    panel.grid.minor = element_blank(),
    panel.grid.major = element_blank(),
    panel.background = element_blank(),
    panel.border = element_blank(),
    axis.line = element_blank(),
    axis.ticks = element_blank(),
    axis.text.x = element_text(size = 13, angle = 45, hjust=1),
    axis.text.y = element_text(size = 13),
    axis.title.x = element_blank(),
    axis.title.y = element_blank()) +
  theme(text = element_text(),
        legend.position="none") +
  scale_x_discrete(position = "bottom")

p.o <- ggplot(df.o, aes(Term1, Term2)) +
  theme_bw(base_size = 12) +
  ggtitle("Aged flies") +
  geom_tile(aes(fill = value), color='white', size = 0.5) +
  coord_equal() +
  geom_text(aes(Term1, Term2, label = value), color = "black", size = 5)  +
  scale_fill_gradient2(low = "#fee6ce", high = "#fee6ce", mid = "#fee6ce", 
                       midpoint = 0.5, limit = c(0,1000000), space = "Lab") +
  theme(plot.background = element_blank(),
        plot.title = element_text(hjust = 0.5),
    panel.grid.minor = element_blank(),
    panel.grid.major = element_blank(),
    panel.background = element_blank(),
    panel.border = element_blank(),
    axis.line = element_blank(),
    axis.ticks = element_blank(),
    axis.text.x = element_text(size = 13, angle = 45, hjust=1),
    axis.text.y = element_text(size = 13),
    axis.title.x = element_blank(),
    axis.title.y = element_blank()) +
  theme(text = element_text(),
        legend.position="none") +
  scale_x_discrete(position = "bottom")

p.similvenn <- ggarrange(p.y, p.o,
                 ncol = 2, nrow = 1,  align = "hv", 
                 widths = 1, heights = 1,
                 common.legend = F)
p.similvenn
```

# Changes in LFC {.tabset}
```{r, warning=FALSE, message=FALSE, echo=FALSE}
sb.genes.lhm.y <- sb.calculator(dataset = dds.lhm, p.threshold = p.threshold, term1 = "FemaleA1", term2 = "MaleA1", population = "LHm")
sb.genes.dah.y <- sb.calculator(dataset = dds.dah, p.threshold = p.threshold, term1 = "FemaleA1", term2 = "MaleA1", population = "Dahomey")
sb.genes.lhm.o <- sb.calculator(dataset = dds.lhm, p.threshold = p.threshold, term1 = "FemaleA2", term2 = "MaleA2", population = "LHm")
sb.genes.dah.o <- sb.calculator(dataset = dds.dah, p.threshold = p.threshold, term1 = "FemaleA2", term2 = "MaleA2", population = "Dahomey")

sb.genes.y <- rbind(sb.genes.lhm.y, sb.genes.dah.y)
sb.genes.o <- rbind(sb.genes.lhm.o, sb.genes.dah.o)

lhm.CD.f <- contrast.calculator(dataset = dds.lhm, term1 = "FemaleA2", term2 = "FemaleA1", population = "LHm")
lhm.CD.m <- contrast.calculator(dataset = dds.lhm, term1 = "MaleA2", term2 = "MaleA1", population = "LHm")
dah.CD.f <- contrast.calculator(dataset = dds.dah, term1 = "FemaleA2", term2 = "FemaleA1", population = "Dahomey")
dah.CD.m <- contrast.calculator(dataset = dds.dah, term1 = "MaleA2", term2 = "MaleA1", population = "Dahomey")

CD.f <- rbind(lhm.CD.f, dah.CD.f)
CD.m <- rbind(lhm.CD.m, dah.CD.m)

dataset <- data.frame(population = CD.f$Population,
                gene = CD.f$Gene,
                bias.class = sb.genes.y$bias,
                bias.class.old = sb.genes.o$bias,
                SB.y = sb.genes.y$log2FoldChange,
                SB.o = sb.genes.o$log2FoldChange,
                CD.f = CD.f$log2FoldChange,
                CD.m = CD.m$log2FoldChange)

#gdata::keep(dataset, sure = TRUE)
```

## Directional
```{r, warning=FALSE, fig.height = 2, fig.width = 6, message=FALSE, echo=FALSE}
dataset.1 <- dataset[complete.cases(dataset),] #[dataset$bias.class != "Undefined",]
dataset.1 <- dataset.1[,c("population", "gene", "bias.class", "CD.f", "CD.m")]
colnames(dataset.1) <- c("Population", "Gene", "Bias", "Female", "Male")
dataset.1 <- dataset.1[complete.cases(dataset.1),]
dataset.1 <- reshape2::melt(dataset.1, id.vars = c("Population", "Gene", "Bias"))
colnames(dataset.1) <- c("Population", "Gene", "Bias", "Sex", "lFC")

plot.graph.lfc <- function(population, yli, ylabyn){
  
  # New facet label names for Sex variable
  supp.labs <- c(paste(population, "Female"),  paste(population, "Male"))
  names(supp.labs) <- c("Female", "Male")

  gex.plot.a <- ggplot(dataset.1[which(dataset.1$Population == population),], aes(x = Bias, y = lFC, fill = Bias)) +
  facet_wrap( ~ Sex, labeller = labeller(Sex = supp.labs)) +
  theme_bw(base_size = 12) +
  geom_boxplot(outlier.shape=NA, notch=T) +
  theme(axis.title.x=element_blank(),
        axis.text.x = element_text(color="black"),
        axis.text.y = element_text(color="black"),
        panel.grid = element_blank(),
        plot.title = element_text(hjust = 0.5),
        legend.position="none",
        legend.background = element_rect(color = "black", size = 0.3, linetype = "solid"),
        legend.text = element_text(size = 12),
        panel.background = element_rect(size = 0.5, linetype = "solid")) +
        #strip.background = element_rect(fill = "white")) +
  scale_fill_manual(limits=c("Female_biased", "Male_biased", "Unbiased"),#, "Undefined"),
                    labels=c("FB", "MB", "UB"), #, "NA"
                    values=c("#fb6a4a", "#6baed6", "#cccccc", "#cccccc")) +
  scale_x_discrete(limits=c("Female_biased", "Male_biased", "Unbiased"),#, "Undefined"),
                   labels=c("FB", "MB", "UB")) + #, "NA"
  geom_hline(yintercept = 0, colour="red", alpha = 0.5, size = 0.5, linetype="longdash") +
  ylim(-yli, yli) +
  ylab(if(ylabyn == T){"log2FC \n (Old - Young)"} else {""}) #+ ggtitle(paste0(population))
gex.plot.a
}

plot.lfc.lhm <- plot.graph.lfc(population = "LHm", yli = 0.15, ylabyn = T)
plot.lfc.dah <- plot.graph.lfc(population = "Dahomey", yli = 2.5, ylabyn = F)

p.1 <- ggarrange(plot.lfc.lhm, plot.lfc.dah,
                 ncol = 2, nrow = 1,  align = "hv", 
                 widths = 1, heights = 1,
                 common.legend = F)

save_plot("Figures/Boxplot_LFC_directional.pdf", p.1, base_width = 10, base_height = 3)
p.1
```

## Absolute changes 
```{r, warning=FALSE, fig.height = 2, fig.width = 6, message=FALSE, echo=FALSE}
plot.graph.lfc <- function(population, yli, ylabyn, y1, y2, y3){
  
  # New facet label names for Sex variable
  supp.labs <- c(paste(population, "Female"),  paste(population, "Male"))
  names(supp.labs) <- c("Female", "Male")
  
  gex.plot.a <- ggplot(dataset.1[which(dataset.1$Population == population),], aes(x = Bias, y = abs(lFC), fill = Bias)) +
  facet_wrap( ~ Sex, labeller = labeller(Sex = supp.labs)) +
  theme_bw(base_size = 12) +
  geom_boxplot(outlier.shape=NA, notch=T) +
  theme(axis.title.x=element_blank(),
        axis.text.x = element_text(color="black"),
        axis.text.y = element_text(color="black"),
        panel.grid = element_blank(),
        plot.title = element_text(hjust = 0.5),
        legend.position="none",
        legend.background = element_rect(color = "black", size = 0.3, linetype = "solid"),
        legend.text = element_text(size = 12),
        panel.background = element_rect(size = 0.5, linetype = "solid")) +
        #strip.background = element_rect(fill = "white")) +
  scale_fill_manual(limits=c("Female_biased", "Male_biased", "Unbiased"),
                    labels=c("FB", "MB", "UB"),
                    values=c("#fb6a4a", "#6baed6", "#cccccc")) +
  scale_x_discrete(limits=c("Female_biased", "Male_biased", "Unbiased"),
                   labels=c("FB", "MB", "UB")) +
  ylim(0, yli) +
  ylab(if(ylabyn == T){"abs log2FC \n (Old - Young)"} else {""}) +
#  ggtitle(paste0(population)) +
  geom_segment(aes(x = 1, y = y1, xend = 1.9, yend = y1)) +
  geom_segment(aes(x = 2.1, y = y2, xend = 3, yend = y2)) +
  geom_segment(aes(x = 1, y = y3, xend = 3, yend = y3)) +
  annotate(geom="text", x=1.5, if(population == "LHm"){y=y1+0.005}else{y=y1+0.1}, label=ifelse(population == "LHm", "", " ")) +
  annotate(geom="text", x=2.5, if(population == "LHm"){y=y2+0.005}else{y=y2+0.1}, label=ifelse(population == "LHm", " ", " ")) +
  annotate(geom="text", x=2, if(population == "LHm"){y=y3+0.005}else{y=y3+0.1}, label=ifelse(population == "LHm", " ", " "))
gex.plot.a
}

plot.lfc.lhm <- plot.graph.lfc(population = "LHm", yli = 0.16, ylabyn = T,
                               y1 = 0.12, y2 = 0.12, y3 = 0.15)
plot.lfc.dah <- plot.graph.lfc(population = "Dahomey", yli = 2.7, ylabyn = F,
                               y1 = 2, y2 = 2, y3 = 2.4)


p.2 <- ggarrange(plot.lfc.lhm, plot.lfc.dah,
                 ncol = 2, nrow = 1,  align = "hv", 
                 widths = 1, heights = 1,
                 common.legend = F)
save_plot("Figures/Boxplot_LFC_abs.pdf", p.2, base_width = 10, base_height = 3)
p.2
```

## Directional Changes along sexualisation/desexualisation axis
This is like "flipping" the change of directions in males when genes are female-biased and viceversa. Good for visualization, not for testing
```{r, warning=FALSE, fig.height = 2, fig.width = 6, message=FALSE, echo=FALSE}
dataset.3 <- dataset[complete.cases(dataset),]
# Flip the sign of change of direction only when Bias and Sex disagree, which means that lFC -> more desexualization
dataset.3$CD.f <- ifelse(dataset.3$bias.class == "Male_biased", -dataset.3$CD.f, dataset.3$CD.f)
dataset.3$CD.m <- ifelse(dataset.3$bias.class == "Female_biased", -dataset.3$CD.m, dataset.3$CD.m)

dataset.3 <- dataset.3[,c("population", "gene", "bias.class", "CD.f", "CD.m")]
colnames(dataset.3) <- c("Population", "Gene", "Bias", "Female", "Male")
#dataset.3 <- dataset.3[complete.cases(dataset.3),]
dataset.3 <- reshape2::melt(dataset.3, id.vars = c("Population", "Gene", "Bias"))
colnames(dataset.3) <- c("Population", "Gene", "Bias", "Sex", "lFC")

plot.graph.lfc <- function(population, yli, ylabyn, y1, y2, y3){
  
  # New facet label names for Sex variable
  supp.labs <- c(paste(population, "Female"),  paste(population, "Male"))
  names(supp.labs) <- c("Female", "Male")
  
  gex.plot.a <- ggplot(dataset.3[which(dataset.3$Population == population),], aes(x = Bias, y = lFC, fill = Bias)) +
  facet_wrap( ~ Sex, labeller = labeller(Sex = supp.labs)) +
  theme_bw(base_size = 12) +
  geom_boxplot(outlier.shape=NA, notch=T) +
  theme(axis.title.x=element_blank(),
        axis.text.x = element_text(color="black"),
        axis.text.y = element_text(color="black"),
        panel.grid = element_blank(),
        plot.title = element_text(hjust = 0.5),
        legend.position="none",
        legend.background = element_rect(color = "black", size = 0.3, linetype = "solid"),
        legend.text = element_text(size = 12),
        panel.background = element_rect(size = 0.5, linetype = "solid")) +
        #strip.background = element_rect(fill = "white")) +
  scale_fill_manual(limits=c("Female_biased", "Male_biased", "Unbiased"),
                    labels=c("FB", "MB", "UB"),
                    values=c("#fb6a4a", "#6baed6", "#cccccc")) +
  scale_x_discrete(limits=c("Female_biased", "Male_biased", "Unbiased"),
                   labels=c("FB", "MB", "UB")) +
  geom_hline(yintercept = 0, colour="red", alpha = 0.5, size = 0.5, linetype="longdash") +
  ylim(-yli, yli) +
  ylab(if(ylabyn == T){"Sexualization \n (Old vs. Young)"} else {""}) +
  #ggtitle(paste0(population)) +
  geom_segment(aes(x = 1, y = y1, xend = 1.9, yend = y1)) +
  geom_segment(aes(x = 2.1, y = y2, xend = 3, yend = y2)) +
  geom_segment(aes(x = 1, y = y3, xend = 3, yend = y3)) +
  annotate(geom="text", x=1.5, if(population == "LHm"){y=y1+0.005}else{y=y1+0.1}, label=" ") +
  annotate(geom="text", x=2.5, if(population == "LHm"){y=y2+0.005}else{y=y2+0.1}, label=" ") +
  annotate(geom="text", x=2, if(population == "LHm"){y=y3+0.005}else{y=y3+0.1}, label=" ")
gex.plot.a
}

plot.lfc.lhm <- plot.graph.lfc(population = "LHm", yli = 0.18, ylabyn = T,
                               y1 = 0.1, y2 = 0.1, y3 = 0.15)
plot.lfc.dah <- plot.graph.lfc(population = "Dahomey", yli =1.8, ylabyn = F,
                               y1 = 1, y2 = 1., y3 = 1.5)

p.3 <- ggarrange(plot.lfc.lhm, plot.lfc.dah,
                 ncol = 2, nrow = 1,  align = "hv", 
                 widths = 1, heights = 1,
                 common.legend = F)
save_plot("Figures/Boxplot_LFC_desexualization.pdf", p.3, base_width = 10, base_height = 3)
p.3
```

## Directional changes where SB genes are SB in either old or young (extended SB set)
```{r, warning=FALSE, fig.height = 2, fig.width = 6, message=FALSE, echo=FALSE}
dataset.y.o <- data.frame(population = CD.f$Population,
                gene = CD.f$Gene,
                # if the bias at young is "Unbiased" try to use bias at old instead (so it becomes biased if old is biased)
                bias.class = ifelse(sb.genes.y$bias != "Unbiased", sb.genes.y$bias, sb.genes.o$bias),
                SB.y = sb.genes.y$log2FoldChange,
                SB.o = sb.genes.o$log2FoldChange,
                CD.f = CD.f$log2FoldChange,
                CD.m = CD.m$log2FoldChange)

dataset.y.o <- dataset.y.o[complete.cases(dataset.y.o),]
dataset.y.o <- dataset.y.o[,c("population", "gene", "bias.class", "CD.f", "CD.m")]
colnames(dataset.y.o) <- c("Population", "Gene", "Bias", "Female", "Male")
dataset.y.o <- dataset.y.o[complete.cases(dataset.y.o),]
dataset.y.o <- reshape2::melt(dataset.y.o, id.vars = c("Population", "Gene", "Bias"))
colnames(dataset.y.o) <- c("Population", "Gene", "Bias", "Sex", "lFC")

plot.graph.lfc <- function(population, yli, ylabyn){
  
  # New facet label names for Sex variable
  supp.labs <- c(paste(population, "Female"),  paste(population, "Male"))
  names(supp.labs) <- c("Female", "Male")
  
  gex.plot.a <- ggplot(dataset.y.o[which(dataset.y.o$Population == population),], aes(x = Bias, y = lFC, fill = Bias)) +
  facet_wrap( ~ Sex, labeller = labeller(Sex = supp.labs)) +
  theme_bw(base_size = 12) +
  geom_boxplot(outlier.shape=NA, notch=T) +
  theme(axis.title.x=element_blank(),
        axis.text.x = element_text(color="black"),
        axis.text.y = element_text(color="black"),
        panel.grid = element_blank(),
        plot.title = element_text(hjust = 0.5),
        legend.position="none",
        legend.background = element_rect(color = "black", size = 0.3, linetype = "solid"),
        legend.text = element_text(size = 12),
        panel.background = element_rect(size = 0.5, linetype = "solid")) +
        #strip.background = element_rect(fill = "white")) +
  scale_fill_manual(limits=c("Female_biased", "Male_biased", "Unbiased"),
                    labels=c("FB", "MB", "UB"),
                    values=c("#fb6a4a", "#6baed6", "#cccccc")) +
  scale_x_discrete(limits=c("Female_biased", "Male_biased", "Unbiased"),
                   labels=c("FB", "MB", "UB")) +
  geom_hline(yintercept = 0, colour="red", alpha = 0.5, size = 0.5, linetype="longdash") +
  ylim(-yli, yli) +
  ylab(if(ylabyn == T){"log2FC \n (Old - Young)"} else {""}) #+ ggtitle(paste0(population))
gex.plot.a
}

plot.lfc.lhm <- plot.graph.lfc(population = "LHm", yli = 0.15, ylabyn = T)
plot.lfc.dah <- plot.graph.lfc(population = "Dahomey", yli = 2.5, ylabyn = F)

p.1 <- ggarrange(plot.lfc.lhm, plot.lfc.dah,
                 ncol = 2, nrow = 1,  align = "hv", 
                 widths = 1, heights = 1,
                 common.legend = F)
save_plot("Figures/Boxplot_LFC_extendedSB.pdf", p.1, base_width = 10, base_height = 3)
p.1
```

## Tissue Specificity 
```{r, warning=FALSE, fig.height = 2, fig.width = 6, message=FALSE, echo=FALSE}
ts <- ts[,c("tau_Male", "tau_Female")]

# LHm
dataset.lhm <- dataset[complete.cases(dataset),] %>% filter(population == "LHm")

lhm.CD <- dataset.lhm[,c("gene", "bias.class", "CD.f", "CD.m")]
colnames(lhm.CD) <- c("Gene", "Bias", "Female", "Male")
lhm.CD <- melt(lhm.CD, id.vars = c("Gene", "Bias"))
ts.lhm <- merge(ts, lhm.CD, by.x=0, by.y = "Gene")
ts.lhm.m <- ts.lhm %>% filter(variable == "Male")
ts.lhm.f <- ts.lhm %>% filter(variable == "Female")
ts.lhm <- rbind(ts.lhm.m, ts.lhm.f)

ts.lhm.lm.m <- lm(value ~ tau_Male,   ts.lhm.m, na.action=na.exclude)
ts.lhm.lm.f <- lm(value ~ tau_Female, ts.lhm.f, na.action=na.exclude)
ts.lhm.lm.m <-as.data.frame(residuals(ts.lhm.lm.m))
ts.lhm.lm.f <-as.data.frame(residuals(ts.lhm.lm.f))
colnames(ts.lhm.lm.m) <- c("Residuals")
colnames(ts.lhm.lm.f) <- c("Residuals")

ts.lhm.lm.mf <- rbind(ts.lhm.lm.m, ts.lhm.lm.f)

residuals.plot.lhm <- ts.lhm[,c("Row.names", "Bias", "variable")]
residuals.plot.lhm <- cbind(residuals.plot.lhm, ts.lhm.lm.mf)
colnames(residuals.plot.lhm) <- c("Gene", "Bias", "Sex", "Residuals")
residuals.plot.lhm <- residuals.plot.lhm[complete.cases(residuals.plot.lhm),]

# Dahomey
dataset.dah <- dataset[complete.cases(dataset),] %>% filter(population == "Dahomey")

dah.CD <- dataset.dah[,c("gene", "bias.class", "CD.f", "CD.m")]
colnames(dah.CD) <- c("Gene", "Bias", "Female", "Male")
dah.CD <- melt(dah.CD, id.vars = c("Gene", "Bias"))
ts.dah <- merge(ts, dah.CD, by.x=0, by.y = "Gene")
ts.dah.m <- ts.dah %>% filter(variable == "Male")
ts.dah.f <- ts.dah %>% filter(variable == "Female")
ts.dah <- rbind(ts.dah.m, ts.dah.f)

ts.dah.lm.m <- lm(value ~ tau_Male,   ts.dah.m, na.action=na.exclude)
ts.dah.lm.f <- lm(value ~ tau_Female, ts.dah.f, na.action=na.exclude)
ts.dah.lm.m <-as.data.frame(residuals(ts.dah.lm.m))
ts.dah.lm.f <-as.data.frame(residuals(ts.dah.lm.f))
colnames(ts.dah.lm.m) <- c("Residuals")
colnames(ts.dah.lm.f) <- c("Residuals")

ts.dah.lm.mf <- rbind(ts.dah.lm.m, ts.dah.lm.f)

residuals.plot.dah <- ts.dah[,c("Row.names", "Bias", "variable")]
residuals.plot.dah <- cbind(residuals.plot.dah, ts.dah.lm.mf)
colnames(residuals.plot.dah) <- c("Gene", "Bias", "Sex", "Residuals")
residuals.plot.dah <- residuals.plot.dah[complete.cases(residuals.plot.dah),]

# New facet label names for Sex variable
supp.labs <- c(paste("LHm", "Female"),  paste("LHm", "Male"))
names(supp.labs) <- c("Female", "Male")

gex.plot.lhm <- ggplot(residuals.plot.lhm, aes(x = Bias, y = Residuals, fill = Bias)) +
facet_wrap( ~ Sex, labeller = labeller(Sex = supp.labs)) +
theme_bw(base_size = 12) +
geom_boxplot(outlier.shape=NA, notch=T) +
theme(axis.title.x=element_blank(),
      axis.text.x = element_text(color="black"),
      axis.text.y = element_text(color="black"),
      panel.grid = element_blank(),
      legend.position="none",
      plot.title = element_text(hjust = 0.5),
      legend.background = element_rect(color = "black", size = 0.3, linetype = "solid"),
      legend.text = element_text(size = 12),
      panel.background = element_rect(size = 0.5, linetype = "solid")) + 
      #strip.background = element_rect(fill = "grey")) +
scale_fill_manual(limits=c("Female_biased", "Male_biased", "Unbiased"),
                  labels=c("FB", "MB", "UB"),
                  values=c("#fb6a4a", "#6baed6", "#cccccc")) +
scale_x_discrete(limits=c("Female_biased", "Male_biased", "Unbiased"),
                 labels=c("FB", "MB", "UB")) +
geom_hline(yintercept = 0, colour="red", alpha = 0.5, size = 0.5, linetype="longdash") +
ylim(-0.15, 0.15) +
ylab("log2FC \n (Old - Young)") +
ggtitle("TS residuals")

supp.labs <- c(paste("Dahomey", "Female"),  paste("Dahomey", "Male"))
names(supp.labs) <- c("Female", "Male")

gex.plot.dah <- ggplot(residuals.plot.dah, aes(x = Bias, y = Residuals, fill = Bias)) +
facet_wrap( ~ Sex, labeller = labeller(Sex = supp.labs)) +
theme_bw(base_size = 12) +
geom_boxplot(outlier.shape=NA, notch=T) +
theme(axis.title.x=element_blank(),
      axis.title.y=element_blank(),
      axis.text.x = element_text(color="black"),
      axis.text.y = element_text(color="black"),
      panel.grid = element_blank(),
      legend.position="none",
      plot.title = element_text(hjust = 0.5),
      legend.background = element_rect(color = "black", size = 0.3, linetype = "solid"),
      legend.text = element_text(size = 12),
      panel.background = element_rect(size = 0.5, linetype = "solid")) +
      #strip.background = element_rect(fill = "grey")) +
scale_fill_manual(limits=c("Female_biased", "Male_biased", "Unbiased"),
                  labels=c("FB", "MB", "UB"),
                  values=c("#fb6a4a", "#6baed6", "#cccccc")) +
scale_x_discrete(limits=c("Female_biased", "Male_biased", "Unbiased"),
                 labels=c("FB", "MB", "UB")) +
geom_hline(yintercept = 0, colour="red", alpha = 0.5, size = 0.5, linetype="longdash") +
ylim(-2.5, 2.5) +
ylab("log2FC \n (Old - Young)") +
ggtitle("TS residuals")

p <- ggarrange(gex.plot.lhm, gex.plot.dah,
                 ncol = 2, nrow = 1,  align = "hv", 
                 widths = 1, heights = 1,
                 common.legend = F)
save_plot("Figures/Boxplot_LFC_TS.pdf", p, base_width = 10, base_height = 3)
p
```

# Test (bayesian approach)
```{r, warning=FALSE, message=FALSE, echo=FALSE, results='hide'}
bayes.test <- function(population, dataset){
  dataset <- dataset[dataset$Bias != "Undefined",]
  dataset <- dataset[which(dataset$Population == population),]
  dataset <- dataset[complete.cases(dataset),]
  m <- stan_glm(lFC ~ Sex * Bias, data = dataset, cores = 8, seed = 100, refresh = 0)
  return(m)
}

bayes.test.group <- function(population, dataset){
  dataset <- dataset[dataset$Bias != "Undefined",]
  dataset <- dataset[which(dataset$Population == population),]
  dataset <- dataset[complete.cases(dataset),]
  dataset$group <- factor(paste0(dataset$Sex, dataset$Bias))
  m <- stan_glm(lFC ~ group, data = dataset, cores = 8, seed = 100, refresh = 0)
  return(m)
}

bayes.test.residuals <- function(dataset){
  dataset <- dataset[dataset$Bias != "Undefined",]
  dataset <- dataset[complete.cases(dataset),]
  m <- stan_glm(Residuals ~ Sex * Bias, data = dataset, cores = 8, seed = 100, refresh = 0)
  return(m)
}

bayes.test.residuals.group <- function(dataset){
  dataset <- dataset[dataset$Bias != "Undefined",]
  dataset <- dataset[complete.cases(dataset),]
  dataset$group <- factor(paste0(dataset$Sex, dataset$Bias))
  m <- stan_glm(Residuals ~ group, data = dataset, cores = 8, seed = 100, refresh = 0)
  return(m)
}

m.lhm <- bayes.test.group(population = "LHm", dataset = dataset.1)
m.dah <- bayes.test.group(population = "Dahomey", dataset = dataset.1)

dataset.1.abs <- dataset.1
dataset.1.abs$lFC <- abs(dataset.1$lFC)
m.dah.abs <- bayes.test.group(population = "Dahomey", dataset = dataset.1.abs)
m.lhm.abs <- bayes.test.group(population = "LHm", dataset = dataset.1.abs)

m.lhm.extendedSB <- bayes.test.group(population = "LHm", dataset = dataset.y.o)
m.dah.extendedSB <- bayes.test.group(population = "Dahomey", dataset = dataset.y.o)
m.lhm.TS <- bayes.test.residuals.group(residuals.plot.lhm[complete.cases(residuals.plot.lhm),])
m.dah.TS <- bayes.test.residuals.group(residuals.plot.dah[complete.cases(residuals.plot.dah),])

bayes.contrasts <- function(m){
  b.con <- as.data.frame(m)
  b.con <- b.con[,c(1:6)]
  colnames(b.con)[1] <- c("Intercept")
  b.con$Female_FB <- b.con$Intercept 
  b.con$Female_MB <- b.con$Intercept + b.con$BiasMale_biased
  b.con$Female_UB <- b.con$Intercept + b.con$BiasUnbiased
  b.con$Male_FB <- b.con$Intercept + b.con$SexMale
  b.con$Male_MB <- b.con$Intercept + b.con$SexMale + b.con$BiasMale_biased + b.con$`SexMale:BiasMale_biased`
  b.con$Male_UB <- b.con$Intercept + b.con$SexMale + b.con$BiasUnbiased + b.con$`SexMale:BiasUnbiased`
  return(b.con)
}

bayes.contrasts.group <- function(m){
  b.con <- as.data.frame(m)
  b.con <- b.con[,c(1:6)]
  colnames(b.con)[1] <- c("Intercept")
  
  b.con$Female_FB <- b.con$Intercept 
  b.con$Female_MB <-  b.con$Intercept + b.con$groupFemaleMale_biased
  b.con$Female_UB <-  b.con$Intercept + b.con$groupFemaleUnbiased
  b.con$Male_FB <-  b.con$Intercept + b.con$groupMaleFemale_biased
  b.con$Male_MB <-  b.con$Intercept + b.con$groupMaleMale_biased
  b.con$Male_UB <-  b.con$Intercept + b.con$groupMaleUnbiased
  return(b.con)
}
```

## LHm
### Model summary LHm
```{r, warning=FALSE, message=FALSE, echo=FALSE}
prior_summary(m.lhm)
intercept <- m.lhm$coefficients["(Intercept)"]
mcmc_areas(m.lhm, transformations = list("groupFemaleMale_biased" = function(x) x + intercept,
                                         "groupFemaleUnbiased" = function(x) x + intercept,
                                         "groupMaleFemale_biased" = function(x) x + intercept,
                                         "groupMaleMale_biased" = function(x) x + intercept,
                                         "groupMaleUnbiased" = function(x) x + intercept))
intercept <- m.lhm.abs$coefficients["(Intercept)"]
mcmc_areas(m.lhm.abs, transformations = list("groupFemaleMale_biased" = function(x) x + intercept,
                                         "groupFemaleUnbiased" = function(x) x + intercept,
                                         "groupMaleFemale_biased" = function(x) x + intercept,
                                         "groupMaleMale_biased" = function(x) x + intercept,
                                         "groupMaleUnbiased" = function(x) x + intercept))
```

### Contrasts LHm directional {.tabset}
#### P <0.05
```{r, warning=FALSE, message=FALSE, echo=FALSE}
contr.bay <- function(model, type, pvalue){
  b.con <- bayes.contrasts.group(model)
  b.con.h <- if(type == "directional"){hypothesis(b.con, 
                                  c("(Male_FB - Male_UB) + (Female_FB - Female_UB) = 0",
                                    "(Male_MB - Male_UB) + (Female_MB - Female_UB) = 0",
                                    "(Male_FB - Male_UB) + (Male_MB - Male_UB) = 0",
                                    "(Female_FB - Female_UB) + (Female_MB - Female_UB) = 0",
                                    "Male_FB - Male_UB = 0",
                                    "Male_MB - Male_UB = 0",
                                    "Female_FB - Female_UB = 0",
                                    "Female_MB - Female_UB = 0",
                                    "(Male_FB-Male_UB) - (Female_MB-Female_UB) = 0",
                                    "(Male_MB-Male_UB) - (Female_FB-Female_UB) = 0"),
                             alpha = pvalue)
                     } else {hypothesis(b.con, 
                                  c("Female_FB = Female_UB",
                                    "Female_MB = Female_UB",
                                    "Male_FB = Male_UB",
                                    "Male_MB = Male_UB",
                                    "Male_FB = Female_FB",
                                    "Male_MB = Female_MB",
                                    "Male_FB = Male_MB",
                                    "Female_FB = Female_MB",
                                    "Male_FB = Female_MB",
                                    "Male_MB = Female_FB"),
                             alpha = pvalue)}
  b.con.h <- as.data.frame(b.con.h$hypothesis)
  b.con.h <- b.con.h[c(1, 8, 2:7)]
  return(b.con.h)
}

get.p <- function(samples){
  if(mean(samples) > 0){
    p <- sum(samples <= 0)/length(samples)
  }else{
    p <- sum(samples >= 0)/length(samples)
  }
  return(max(p*2, (1/4000)*2))
}

b.con.h <- contr.bay(model = m.lhm,
                     type = "directional",
                     pvalue = 0.05)

b.con.samples <- bayes.contrasts.group(m.lhm)

b.con.h$Pmcmc <- c(get.p((b.con.samples$Male_FB - b.con.samples$Male_UB) + (b.con.samples$Female_FB - b.con.samples$Female_UB)),
get.p((b.con.samples$Male_MB - b.con.samples$Male_UB) + (b.con.samples$Female_MB - b.con.samples$Female_UB)),
get.p((b.con.samples$Male_FB - b.con.samples$Male_UB) + (b.con.samples$Male_MB - b.con.samples$Male_UB)),
get.p((b.con.samples$Female_FB - b.con.samples$Female_UB) + (b.con.samples$Female_MB - b.con.samples$Female_UB)),
get.p((b.con.samples$Male_FB - b.con.samples$Male_UB)),
get.p((b.con.samples$Male_MB - b.con.samples$Male_UB)),
get.p((b.con.samples$Female_FB - b.con.samples$Female_UB)),
get.p((b.con.samples$Female_MB - b.con.samples$Female_UB)),
get.p((b.con.samples$Male_FB - b.con.samples$Male_UB) - (b.con.samples$Female_MB - b.con.samples$Female_UB)),
get.p((b.con.samples$Male_MB - b.con.samples$Male_UB) - (b.con.samples$Female_FB - b.con.samples$Female_UB)))

b.con.h <- subset(b.con.h,select=-c(Evid.Ratio, Post.Prob, Star))
write.table(b.con.h, "Tables/bayes_directional_lhm.csv", quote = FALSE, sep = ",", row.names = FALSE)
b.con.h
```

### Contrasts LHm abs {.tabset}
#### P <0.05
```{r, warning=FALSE, message=FALSE, echo=FALSE}
b.con.h <- contr.bay(model = m.lhm.abs,
                     type = "absolute",
                     pvalue = 0.05)

b.con.samples <- bayes.contrasts.group(m.lhm.abs)
b.con.h$Pmcmc <- c(get.p(b.con.samples$Female_FB - b.con.samples$Female_UB),
               get.p(b.con.samples$Female_MB - b.con.samples$Female_UB),
               get.p(b.con.samples$Male_FB - b.con.samples$Male_UB),
               get.p(b.con.samples$Male_MB - b.con.samples$Male_UB),
               get.p(b.con.samples$Male_FB - b.con.samples$Female_MB),
               get.p(b.con.samples$Male_MB - b.con.samples$Female_MB),
               get.p(b.con.samples$Male_FB - b.con.samples$Male_MB),
               get.p(b.con.samples$Female_FB - b.con.samples$Female_MB),
               get.p(b.con.samples$Male_FB - b.con.samples$Female_MB),
               get.p(b.con.samples$Male_MB - b.con.samples$Female_FB))
#b.con.h <- subset(b.con.h,select=-c(Evid.Ratio, Post.Prob))
b.con.h <- subset(b.con.h,select=-c(Evid.Ratio, Post.Prob, Star))
write.table(b.con.h, "Tables/bayes_absolute_lhm.csv", quote = FALSE, sep = ",", row.names = FALSE)
b.con.h
```

### Contrasts LHm directional - extended SB {.tabset}
#### P <0.05
```{r, warning=FALSE, message=FALSE, echo=FALSE}
b.con.h <- contr.bay(model = m.lhm.extendedSB,
                     type = "directional",
                     pvalue = 0.05)

b.con.samples <- bayes.contrasts.group(m.lhm.extendedSB)

b.con.h$Pmcmc <- c(get.p((b.con.samples$Male_FB - b.con.samples$Male_UB) + (b.con.samples$Female_FB - b.con.samples$Female_UB)),
get.p((b.con.samples$Male_MB - b.con.samples$Male_UB) + (b.con.samples$Female_MB - b.con.samples$Female_UB)),
get.p((b.con.samples$Male_FB - b.con.samples$Male_UB) + (b.con.samples$Male_MB - b.con.samples$Male_UB)),
get.p((b.con.samples$Female_FB - b.con.samples$Female_UB) + (b.con.samples$Female_MB - b.con.samples$Female_UB)),
get.p((b.con.samples$Male_FB - b.con.samples$Male_UB)),
get.p((b.con.samples$Male_MB - b.con.samples$Male_UB)),
get.p((b.con.samples$Female_FB - b.con.samples$Female_UB)),
get.p((b.con.samples$Female_MB - b.con.samples$Female_UB)),
get.p((b.con.samples$Male_FB - b.con.samples$Male_UB) - (b.con.samples$Female_MB - b.con.samples$Female_UB)),
get.p((b.con.samples$Male_MB - b.con.samples$Male_UB) - (b.con.samples$Female_FB - b.con.samples$Female_UB)))
b.con.h <- subset(b.con.h,select=-c(Evid.Ratio, Post.Prob, Star))
write.table(b.con.h, "Tables/bayes_extendedSB_lhm.csv", quote = FALSE, sep = ",", row.names = FALSE)
b.con.h
```

### Contrasts LHm directional - TS {.tabset}
#### P <0.05
```{r, warning=FALSE, message=FALSE, echo=FALSE}
b.con.h <- contr.bay(model = m.lhm.TS,
                     type = "directional",
                     pvalue = 0.05)

b.con.samples <- bayes.contrasts.group(m.lhm.TS)

b.con.h$Pmcmc <- c(get.p((b.con.samples$Male_FB - b.con.samples$Male_UB) + (b.con.samples$Female_FB - b.con.samples$Female_UB)),
get.p((b.con.samples$Male_MB - b.con.samples$Male_UB) + (b.con.samples$Female_MB - b.con.samples$Female_UB)),
get.p((b.con.samples$Male_FB - b.con.samples$Male_UB) + (b.con.samples$Male_MB - b.con.samples$Male_UB)),
get.p((b.con.samples$Female_FB - b.con.samples$Female_UB) + (b.con.samples$Female_MB - b.con.samples$Female_UB)),
get.p((b.con.samples$Male_FB - b.con.samples$Male_UB)),
get.p((b.con.samples$Male_MB - b.con.samples$Male_UB)),
get.p((b.con.samples$Female_FB - b.con.samples$Female_UB)),
get.p((b.con.samples$Female_MB - b.con.samples$Female_UB)),
get.p((b.con.samples$Male_FB - b.con.samples$Male_UB) - (b.con.samples$Female_MB - b.con.samples$Female_UB)),
get.p((b.con.samples$Male_MB - b.con.samples$Male_UB) - (b.con.samples$Female_FB - b.con.samples$Female_UB)))
b.con.h <- subset(b.con.h,select=-c(Evid.Ratio, Post.Prob, Star))
write.table(b.con.h, "Tables/bayes_TS_lhm.csv", quote = FALSE, sep = ",", row.names = FALSE)
b.con.h
```

## Dahomey
### Model summary Dahomey
```{r, warning=FALSE, message=FALSE, echo=FALSE}
prior_summary(m.dah)
intercept <- m.dah$coefficients["(Intercept)"]
mcmc_areas(m.dah, transformations = list("groupFemaleMale_biased" = function(x) x + intercept,
                                         "groupFemaleUnbiased" = function(x) x + intercept,
                                         "groupMaleFemale_biased" = function(x) x + intercept,
                                         "groupMaleMale_biased" = function(x) x + intercept,
                                         "groupMaleUnbiased" = function(x) x + intercept))
intercept <- m.dah.abs$coefficients["(Intercept)"]
mcmc_areas(m.dah.abs, transformations = list("groupFemaleMale_biased" = function(x) x + intercept,
                                         "groupFemaleUnbiased" = function(x) x + intercept,
                                         "groupMaleFemale_biased" = function(x) x + intercept,
                                         "groupMaleMale_biased" = function(x) x + intercept,
                                         "groupMaleUnbiased" = function(x) x + intercept))
```

### Contrasts Dahomey directional {.tabset}
#### P <0.05
```{r, warning=FALSE, message=FALSE, echo=FALSE}
b.con.h <- contr.bay(model = m.dah,
                     type = "directional",
                     pvalue = 0.05)

b.con.samples <- bayes.contrasts.group(m.dah)

b.con.h$Pmcmc <- c(get.p((b.con.samples$Male_FB - b.con.samples$Male_UB) + (b.con.samples$Female_FB - b.con.samples$Female_UB)),
get.p((b.con.samples$Male_MB - b.con.samples$Male_UB) + (b.con.samples$Female_MB - b.con.samples$Female_UB)),
get.p((b.con.samples$Male_FB - b.con.samples$Male_UB) + (b.con.samples$Male_MB - b.con.samples$Male_UB)),
get.p((b.con.samples$Female_FB - b.con.samples$Female_UB) + (b.con.samples$Female_MB - b.con.samples$Female_UB)),
get.p((b.con.samples$Male_FB - b.con.samples$Male_UB)),
get.p((b.con.samples$Male_MB - b.con.samples$Male_UB)),
get.p((b.con.samples$Female_FB - b.con.samples$Female_UB)),
get.p((b.con.samples$Female_MB - b.con.samples$Female_UB)),
get.p((b.con.samples$Male_FB - b.con.samples$Male_UB) - (b.con.samples$Female_MB - b.con.samples$Female_UB)),
get.p((b.con.samples$Male_MB - b.con.samples$Male_UB) - (b.con.samples$Female_FB - b.con.samples$Female_UB)))
b.con.h <- subset(b.con.h,select=-c(Evid.Ratio, Post.Prob, Star))
write.table(b.con.h, "Tables/bayes_directional_dah.csv", quote = FALSE, sep = ",", row.names = FALSE)

b.con.h
```

### Contrasts Dahomey abs {.tabset}
#### P <0.05
```{r, warning=FALSE, message=FALSE, echo=FALSE}
b.con.h <- contr.bay(model = m.dah.abs,
                     type = "absolute",
                     pvalue = 0.05)

b.con.samples <- bayes.contrasts.group(m.dah.abs)
b.con.h$Pmcmc <- c(get.p(b.con.samples$Female_FB- b.con.samples$Female_UB),
               get.p(b.con.samples$Female_MB - b.con.samples$Female_UB),
               get.p(b.con.samples$Male_FB - b.con.samples$Male_UB),
               get.p(b.con.samples$Male_MB - b.con.samples$Male_UB),
               get.p(b.con.samples$Male_FB - b.con.samples$Female_MB),
               get.p(b.con.samples$Male_MB - b.con.samples$Female_MB),
               get.p(b.con.samples$Male_FB - b.con.samples$Male_MB),
               get.p(b.con.samples$Female_FB - b.con.samples$Female_MB),
               get.p(b.con.samples$Male_FB - b.con.samples$Female_MB),
               get.p(b.con.samples$Male_MB - b.con.samples$Female_FB))
b.con.h <- subset(b.con.h,select=-c(Evid.Ratio, Post.Prob, Star))
write.table(b.con.h, "Tables/bayes_absolute_dah.csv", quote = FALSE, sep = ",", row.names = FALSE)

b.con.h
```

### Contrasts Dah directional - extended SB {.tabset}
#### P <0.05
```{r, warning=FALSE, message=FALSE, echo=FALSE}
b.con.h <- contr.bay(model = m.dah.extendedSB,
                     type = "directional",
                     pvalue = 0.05)

b.con.samples <- bayes.contrasts.group(m.dah.extendedSB)

b.con.h$Pmcmc <- c(get.p((b.con.samples$Male_FB - b.con.samples$Male_UB) + (b.con.samples$Female_FB - b.con.samples$Female_UB)),
get.p((b.con.samples$Male_MB - b.con.samples$Male_UB) + (b.con.samples$Female_MB - b.con.samples$Female_UB)),
get.p((b.con.samples$Male_FB - b.con.samples$Male_UB) + (b.con.samples$Male_MB - b.con.samples$Male_UB)),
get.p((b.con.samples$Female_FB - b.con.samples$Female_UB) + (b.con.samples$Female_MB - b.con.samples$Female_UB)),
get.p((b.con.samples$Male_FB - b.con.samples$Male_UB)),
get.p((b.con.samples$Male_MB - b.con.samples$Male_UB)),
get.p((b.con.samples$Female_FB - b.con.samples$Female_UB)),
get.p((b.con.samples$Female_MB - b.con.samples$Female_UB)),
get.p((b.con.samples$Male_FB - b.con.samples$Male_UB) - (b.con.samples$Female_MB - b.con.samples$Female_UB)),
get.p((b.con.samples$Male_MB - b.con.samples$Male_UB) - (b.con.samples$Female_FB - b.con.samples$Female_UB)))
b.con.h <- subset(b.con.h,select=-c(Evid.Ratio, Post.Prob, Star))
write.table(b.con.h, "Tables/bayes_extendedSB_dah.csv", quote = FALSE, sep = ",", row.names = FALSE)

b.con.h
```

### Contrasts Dah directional - TS {.tabset}
#### P <0.05
```{r, warning=FALSE, message=FALSE, echo=FALSE}
b.con.h <- contr.bay(model = m.dah.TS,
                     type = "directional",
                     pvalue = 0.05)

b.con.samples <- bayes.contrasts.group(m.dah.TS)

b.con.h$Pmcmc <- c(get.p((b.con.samples$Male_FB - b.con.samples$Male_UB) + (b.con.samples$Female_FB - b.con.samples$Female_UB)),
get.p((b.con.samples$Male_MB - b.con.samples$Male_UB) + (b.con.samples$Female_MB - b.con.samples$Female_UB)),
get.p((b.con.samples$Male_FB - b.con.samples$Male_UB) + (b.con.samples$Male_MB - b.con.samples$Male_UB)),
get.p((b.con.samples$Female_FB - b.con.samples$Female_UB) + (b.con.samples$Female_MB - b.con.samples$Female_UB)),
get.p((b.con.samples$Male_FB - b.con.samples$Male_UB)),
get.p((b.con.samples$Male_MB - b.con.samples$Male_UB)),
get.p((b.con.samples$Female_FB - b.con.samples$Female_UB)),
get.p((b.con.samples$Female_MB - b.con.samples$Female_UB)),
get.p((b.con.samples$Male_FB - b.con.samples$Male_UB) - (b.con.samples$Female_MB - b.con.samples$Female_UB)),
get.p((b.con.samples$Male_MB - b.con.samples$Male_UB) - (b.con.samples$Female_FB - b.con.samples$Female_UB)))
b.con.h <- subset(b.con.h,select=-c(Evid.Ratio, Post.Prob, Star))
write.table(b.con.h, "Tables/bayes_TS_dah.csv", quote = FALSE, sep = ",", row.names = FALSE)

b.con.h
```

## Coefficient of variation 
### Graph
```{r, warning=FALSE, fig.height = 3, fig.width = 3, message=FALSE, echo=FALSE}
cv.calculator <- function(vstdata){
  vstdata <- vstdata
  vstdata$combined1 = factor(paste0(vstdata$Sex, "_", vstdata$Age))
  rldPerLvl_sex <- sapply(levels(vstdata$combined1),  
                        function(x){
                          aaa <- rowSds(assay(vstdata)[,vstdata$combined1 == x], na.rm = TRUE) /   rowMeans(assay(vstdata)[,vstdata$combined1 == x], na.rm = TRUE)
                          aaa <- setDT(as.data.frame(aaa), keep.rownames = TRUE)[]
                          aaa <- aaa[,c("aaa")]
                          return(aaa)},
                        simplify = FALSE,USE.NAMES = TRUE)
  vstdata <- do.call(cbind, rldPerLvl_sex)
  vstdata <- cbind(dataset[,c(2,3)], vstdata)
  names(vstdata) <- gsub("\\..*","", names(vstdata))
  vstdata <- melt(vstdata, id.vars = c("gene", "bias"))
  vstdata <- vstdata[complete.cases(vstdata),]
  #vstdata <- vstdata[order(variable, gene),]
  vstdata$sex <- NA
  vstdata$sex <- ifelse(grepl("Female_",vstdata$variable),"Female", "Male")
  vstdata$variable <- gsub(".*_","",vstdata$variable)
  return(vstdata)
}

plot.cv <- function(vstdata, ylimi, population){
  # New facet label names for Sex variable
  supp.labs <- c(paste(population, "Female"),  paste(population, "Male"))
  names(supp.labs) <- c("Female", "Male")
  
  p1 <- ggplot(vstdata, aes(x = variable, y = value)) +
    facet_wrap( ~ sex, labeller = labeller(sex = supp.labs)) +
    theme_bw(base_size = 15) + 
    geom_boxplot(outlier.colour="black", notch=T, outlier.shape=NA) +
    theme(axis.title.x=element_blank(),
        axis.text.x = element_text(color="black"),
        axis.text.y = element_text(color="black"),
        panel.grid = element_blank())+
    theme(legend.position="none",
        legend.background = element_rect(color = "black", size = 0.3, linetype = "solid"),
        legend.text = element_text(size = 12),
        panel.background = element_rect(size = 0.5, linetype = "solid"),
        #strip.background = element_rect(fill = "grey"),
        axis.text.x = element_text(angle = 90, hjust = 1)) +
    geom_hline(data=data.frame(value= median(subset(vstdata, variable == "A1" & sex == "Female")$value), sex="Female"), aes(yintercept=value),linetype="longdash", color = "red", size=1) +
    geom_hline(data=data.frame(value= median(subset(vstdata, variable == "A1" & sex == "Male")$value), sex="Male"), aes(yintercept=value),linetype="longdash", color = "red", size=1) +
    scale_x_discrete(limits=c("A1", "A2"),
                   labels=c("Young", "Old")) +
    ylab("CV normalized counts") +
    ylim(0,ylimi) #+ ggtitle(paste0(population))
  return(p1)
}

var.lhm <- cv.calculator(vstdata.lhm)
var.dah <- cv.calculator(vstdata.dah)
p1 <- plot.cv(var.lhm, ylimi = 0.02, population = "LHm")
p2 <- plot.cv(var.dah, ylimi = 0.15, population = "Dahomey")

p <- ggarrange(p1, p2,
               ncol = 1, nrow = 2,  align = "hv",
               widths = 1, heights = 1,
               common.legend = F)
save_plot("Figures/Coeff_var.pdf", p, base_width = 5, base_height = 5)
p
```

### Test {.tabset}
#### Model LHm
```{r, warning=FALSE, message=FALSE, echo=FALSE}
model <- lmer(value ~ variable * sex * (1|bias), data = var.lhm)
Anova(model)
```

#### Contrasts LHm
```{r, warning=FALSE, message=FALSE, echo=FALSE}
m1 <- emmeans(model, "variable", by = c("sex"))
pairs(m1)
```

#### Model Dahomey
```{r, warning=FALSE, message=FALSE, echo=FALSE}
model <- lmer(value ~ variable * sex * (1|bias), data = var.dah)
Anova(model)
```

#### Contrasts Dahomey
```{r, warning=FALSE, message=FALSE, echo=FALSE}
m1 <- emmeans(model, "variable", by = c("sex"))
pairs(m1)
```

# Are males the more sensitive sex – do SB genes change more in males?
In this graph CD is regressed over abs(SB). Panels are split by bias.class and population. Lines represent females (red) and males (blue).
```{r, warning=FALSE, fig.height = 2, fig.width = 6, message=FALSE, echo=FALSE}
dataset.4 <- dataset
dataset.4 <- dataset.4[which(dataset.4$bias.class != "Unbiased"),]
#dataset.4 <- dataset.4[which(dataset.4$bias.class != "Undefined"),]
dataset.4$CD.f <- ifelse(dataset.4$bias.class == "Male_biased", -dataset.4$CD.f, dataset.4$CD.f)
dataset.4$CD.m <- ifelse(dataset.4$bias.class == "Female_biased", -dataset.4$CD.m, dataset.4$CD.m)

dataset.4 <- dataset.4[complete.cases(dataset.4),]
dataset.4 <- dataset.4[,c("population", "gene", "bias.class", "SB.y", "CD.f", "CD.m")]
colnames(dataset.4) <- c("Population", "Gene", "Bias", "SB", "Females", "Males")
dataset.4 <- reshape2::melt(dataset.4, id.vars = c("Population", "Gene", "Bias", "SB"))
colnames(dataset.4) <- c("Population", "Gene", "Bias", "SB.lFC", "Sex", "CD.lFC")
dataset.4$Bias <- gsub("_", " ", dataset.4$Bias)

# New facet label names for Sex variable
supp.labs <- c(paste("LHm", "Female"),  paste("LHm", "Male"))
names(supp.labs) <- c("Females", "Males")
d.4.lhm <- dataset.4[which(dataset.4$Population == "LHm"),]
gex.plot1 <- ggplot(d.4.lhm, aes(y=CD.lFC, x=abs(SB.lFC), color = Bias))  +
    facet_grid(~ Sex, labeller = labeller(Sex = supp.labs)) +
    theme_bw(base_size = 12) +
    #ggtitle("LHm") +
    geom_point(size = 1, alpha = 0.5) +
    xlab("Sex-bias (abs log2FC)") +
    ylab("Sexualization \n (Old vs. Young)") +
    theme(legend.position="none",
        legend.background = element_rect(color = "black", size = 0.3, linetype = "solid"),
          legend.text = element_text(size = 12),
          axis.text.x = element_text(color="black"),
          axis.text.y = element_text(color="black"),
          panel.background = element_rect(size = 0.5, linetype = "solid"),
          panel.grid.major = element_blank(), 
          panel.grid.minor = element_blank(),
          plot.title = element_text(hjust = 0.5),
          axis.title=element_text(size=12)) +
    geom_smooth(method=lm, se=TRUE, level = 0.95, fullrange=TRUE, data = filter(d.4.lhm, Bias == "Female biased"), color = "#f03b20") +
    geom_smooth(method=lm, se=TRUE, level = 0.95, fullrange=TRUE, data = filter(d.4.lhm, Bias == "Male biased"), color = "#2c7fb8")+
    stat_poly_eq(formula = y ~ x, 
               aes(label = paste(..eq.label.., sep = "~~~")), 
               parse = TRUE, vstep = 0.1, coef.digits = 2) +
    scale_colour_manual(name = "Legend", values=c("#fb6a4a", "#6baed6"),
                        labels = c("Female biased", "Male biased"), 
                        breaks = c("Female biased", "Male biased")) +
    ylim(-0.75,0.75) +
    xlim(0,0.65)

supp.labs <- c(paste("Dahomey", "Female"),  paste("Dahomey", "Male"))
names(supp.labs) <- c("Females", "Males")

d.4.dah <- dataset.4[which(dataset.4$Population == "Dahomey"),]
gex.plot2 <- ggplot(d.4.dah, aes(y=CD.lFC, x=abs(SB.lFC), color = Bias))  +
    facet_grid(~ Sex, labeller = labeller(Sex = supp.labs)) +
    theme_bw(base_size = 12) +
    geom_point(size = 1, alpha = 0.5) +
    xlab("Sex-bias (abs log2FC)") +
    ylab("") +
    theme(legend.position="none",
          legend.background = element_rect(color = "black", size = 0.3, linetype = "solid"),
          legend.text = element_text(size = 12),
          axis.text.x = element_text(color="black"),
          axis.text.y = element_text(color="black"),
          panel.background = element_rect(size = 0.5, linetype = "solid"),
          panel.grid.major = element_blank(), 
          panel.grid.minor = element_blank(),
          plot.title = element_text(hjust = 0.5),
          axis.title=element_text(size=12)) +
    geom_smooth(method=lm, se=FALSE, level = 0.95, fullrange=TRUE, data = filter(d.4.dah, Bias == "Female biased"), color = "#f03b20") +
    geom_smooth(method=lm, se=FALSE, level = 0.95, fullrange=TRUE, data = filter(d.4.dah, Bias == "Male biased"), color = "#2c7fb8") +
    stat_poly_eq(formula = y ~ x, 
               aes(label = paste(..eq.label.., sep = "~~~")), 
               parse = TRUE, vstep = 0.1, coef.digits = 2) +  
    scale_colour_manual(name = "Legend", values=c("#fb6a4a", "#6baed6"),
                        labels = c("Female biased", "Male biased"), 
                        breaks = c("Female biased", "Male biased")) +
    ylim(-4,4) +
    xlim(0,3.5) 

p <- ggarrange(gex.plot1, gex.plot2,
                 ncol = 2, nrow = 1,  align = "hv", 
                 widths = 1, heights = 1,
                 common.legend = F)

save_plot("Figures/CD_SB.pdf", p, base_width = 10, base_height = 3)
p
```

## Test {.tabset}

```{r}
print.lm <- function(model){
  model.summary <- summary(model)
  model.model <- substr(toString(model.summary$call$subset), 4, 1000)
  model.predictor <- format(terms(model))#model.summary$call$formula
  
  coeff.row <- dim(model.summary$coefficients)[1]
  model.coefficient <- model.summary$coefficients[coeff.row,1]
  model.SE <- model.summary$coefficients[coeff.row,2]
  model.p <- model.summary$coefficients[coeff.row,4]
  model.fstat <- model.summary$fstatistic[1]
  model.numdf <- model.summary$fstatistic[2]
  model.dendf <- model.summary$fstatistic[3]
  model.df <- paste0("F(", model.numdf, ", ", model.dendf, ") = ", round(model.fstat, 2))
  
  data.frame(Model = model.model, Formula = model.predictor, Coefficient = model.coefficient, S.E. = model.SE, "p-value" = model.p, "F-stat" = model.df)
}
```


### LHm Female
```{r, warning=FALSE, message=FALSE, echo=FALSE}
model1.f.lhm <- lm(CD.lFC ~ abs(SB.lFC), data = dataset.4, subset = c(Sex == "Females" & Bias == "Female biased" & Population == "LHm"))
model2.f.lhm <- lm(CD.lFC ~ abs(SB.lFC), data = dataset.4, subset = c(Sex == "Females" & Bias == "Male biased" & Population == "LHm"))
summary(model1.f.lhm)
summary(model2.f.lhm)
test.incline.by.bias.f.lhm <- lm(CD.lFC ~ Bias * abs(SB.lFC), data = dataset.4, subset = c(Sex == "Females" & Population == "LHm"))
summary(test.incline.by.bias.f.lhm)
```

### LHm Male
```{r, warning=FALSE, message=FALSE, echo=FALSE}
model1.m.lhm <- lm(CD.lFC ~ abs(SB.lFC), data = dataset.4, subset = c(Sex == "Males" & Bias == "Female biased" & Population == "LHm"))
model2.m.lhm <- lm(CD.lFC ~ abs(SB.lFC), data = dataset.4, subset = c(Sex == "Males" & Bias == "Male biased" & Population == "LHm"))
summary(model1.m.lhm)
summary(model2.m.lhm)
test.incline.by.bias.m.lhm <- lm(CD.lFC ~ Bias * abs(SB.lFC), data = dataset.4, subset = c(Sex == "Males" & Population == "LHm"))
summary(test.incline.by.bias.m.lhm)
```

### LHm Female biased
```{r}
test.incline.by.sex.fb.lhm <- lm(CD.lFC ~ Sex * abs(SB.lFC), data = dataset.4, subset = c(Bias == "Female biased" & Population == "LHm"))
summary(test.incline.by.sex.fb.lhm)
```

### LHm Male biased
```{r}
test.incline.by.sex.mb.lhm <- lm(CD.lFC ~ Sex * abs(SB.lFC), data = dataset.4, subset = c(Bias == "Male biased" & Population == "LHm"))
summary(test.incline.by.sex.mb.lhm)
```
### LHm cis/trans
```{r}
dataset.4$group <- paste0(dataset.4$Sex, dataset.4$Bias)
test.incline.by.sex.and.bias.1.lhm <- lm(CD.lFC ~ group * abs(SB.lFC), data = dataset.4, subset = c((group == "FemalesFemale biased" | group == "MalesMale biased") & Population == "LHm"))
summary(test.incline.by.sex.and.bias.1.lhm)

test.incline.by.sex.and.bias.2.lhm <- lm(CD.lFC ~ group * abs(SB.lFC), data = dataset.4, subset = c((group == "MalesFemale biased" | group == "FemalesMale biased") & Population == "LHm"))
summary(test.incline.by.sex.and.bias.2.lhm)
```
### Table LHm
```{r}
regression.models.lhm <- do.call(rbind, lapply(list(model1.f.lhm, model2.f.lhm, test.incline.by.bias.f.lhm, 
                           model1.m.lhm, model2.m.lhm, test.incline.by.bias.m.lhm, 
                           test.incline.by.sex.fb.lhm, test.incline.by.sex.mb.lhm,
                           test.incline.by.sex.and.bias.1.lhm, test.incline.by.sex.and.bias.2.lhm), print.lm))
regression.models.lhm
write.table(regression.models.lhm, "Tables/regression_models_lhm.csv", quote = FALSE, sep = ",", row.names = FALSE)
```

### Dahomey Female
```{r, warning=FALSE, message=FALSE, echo=FALSE}
model1.f.dah <- lm(CD.lFC ~ abs(SB.lFC), data = dataset.4, subset = c(Sex == "Females" & Bias == "Female biased" & Population == "Dahomey"))
model2.f.dah <- lm(CD.lFC ~ abs(SB.lFC), data = dataset.4, subset = c(Sex == "Females" & Bias == "Male biased" & Population == "Dahomey"))
summary(model1.f.dah)
summary(model2.f.dah)

test.incline.by.bias.f.dah <- lm(CD.lFC ~ Bias * abs(SB.lFC), data = dataset.4, subset = c(Sex == "Females" & Population == "Dahomey"))
summary(test.incline.by.bias.f.dah)
```

### Dahomey Male
```{r, warning=FALSE, message=FALSE, echo=FALSE}
model1.m.dah <- lm(CD.lFC ~ abs(SB.lFC), data = dataset.4, subset = c(Sex == "Males" & Bias == "Female biased" & Population == "Dahomey"))
model2.m.dah <- lm(CD.lFC ~ abs(SB.lFC), data = dataset.4, subset = c(Sex == "Males" & Bias == "Male biased" & Population == "Dahomey"))
summary(model1.m.dah)
summary(model2.m.dah)
test.incline.by.bias.m.dah <- lm(CD.lFC ~ Bias * abs(SB.lFC), data = dataset.4, subset = c(Sex == "Males" & Population == "Dahomey"))
summary(test.incline.by.bias.m.dah)
```

### Dahomey Female biased
```{r}
test.incline.by.sex.fb.dah <- lm(CD.lFC ~ Sex * abs(SB.lFC), data = dataset.4, subset = c(Bias == "Female biased" & Population == "Dahomey"))
summary(test.incline.by.sex.fb.dah)
```

### Dahomey Male biased
```{r}
test.incline.by.sex.mb.dah <- lm(CD.lFC ~ Sex * abs(SB.lFC), data = dataset.4, subset = c(Bias == "Male biased" & Population == "Dahomey"))
summary(test.incline.by.sex.mb.dah)
```

### Dahomey cis/trans
```{r}
dataset.4$group <- paste0(dataset.4$Sex, dataset.4$Bias)
test.incline.by.sex.and.bias.1.dah <- lm(CD.lFC ~ group * abs(SB.lFC), data = dataset.4, subset = c((group == "FemalesFemale biased" | group == "MalesMale biased") & Population == "Dahomey"))
summary(test.incline.by.sex.and.bias.1.dah)

test.incline.by.sex.and.bias.2.dah <- lm(CD.lFC ~ group * abs(SB.lFC), data = dataset.4, subset = c((group == "MalesFemale biased" | group == "FemalesMale biased") & Population == "Dahomey"))
summary(test.incline.by.sex.and.bias.2.dah)
```
### Table LHm
```{r}
regression.models.dahomey <- do.call(rbind, lapply(list(model1.f.dah, model2.f.dah, test.incline.by.bias.f.dah, 
                           model1.m.dah, model2.m.dah, test.incline.by.bias.m.dah, 
                           test.incline.by.sex.fb.dah, test.incline.by.sex.mb.dah,
                           test.incline.by.sex.and.bias.1.dah, test.incline.by.sex.and.bias.2.dah), print.lm))
regression.models.dahomey
write.table(regression.models.dahomey, "Tables/regression_models_dahomey.csv", quote = FALSE, sep = ",", row.names = FALSE)
```

### LHm/Dahomey incline comparison
```{r}
test.incline.by.population.f.fb <- lm(CD.lFC ~ Population * abs(SB.lFC), data = dataset.4, subset = c(Bias == "Female biased" & Sex == "Females"))
summary(test.incline.by.population.f.fb)
test.incline.by.population.f.mb <- lm(CD.lFC ~ Population * abs(SB.lFC), data = dataset.4, subset = c(Bias == "Male biased" & Sex == "Females"))
summary(test.incline.by.population.f.mb)
test.incline.by.population.m.fb <- lm(CD.lFC ~ Population * abs(SB.lFC), data = dataset.4, subset = c(Bias == "Female biased" & Sex == "Males"))
summary(test.incline.by.population.m.fb)
test.incline.by.population.m.mb <- lm(CD.lFC ~ Population * abs(SB.lFC), data = dataset.4, subset = c(Bias == "Male biased" & Sex == "Males"))
summary(test.incline.by.population.m.mb)
```

### Table LHm/Dahomey
```{r}
incline.by.population <- do.call(rbind, lapply(list(test.incline.by.population.f.fb, test.incline.by.population.f.mb, test.incline.by.population.m.fb, test.incline.by.population.m.mb), print.lm))
write.table(incline.by.population, "Tables/incline_by_population.csv", quote = FALSE, sep = ",", row.names = FALSE)
incline.by.population
```


#	Do SB genes change in the same direction in the two sexes? 
```{r, warning=FALSE, fig.height = 3, fig.width = 6, message=FALSE, echo=FALSE}
dataset.6 <- subset(dataset, bias.class != 'Unbiased')
dataset.6 <- dataset[complete.cases(dataset),]
#dataset.6 <- subset(dataset.6, bias.class != 'Undefined')
dataset.6$Female <- ifelse(dataset.6$bias.class == "Female_biased", dataset.6$CD.f, -dataset.6$CD.f)
dataset.6$Male <- ifelse(dataset.6$bias.class == "Female_biased", dataset.6$CD.m, -dataset.6$CD.m)
dataset.6$angle <- atan2((dataset.6$Female), (dataset.6$Male))
dataset.6$angle <- dataset.6$angle * 180/pi
dataset.6$angle <- ifelse(dataset.6$angle <= 0, dataset.6$angle + 360, dataset.6$angle)
#dataset.6$angle <- ifelse(dataset.6$angle > 180, dataset.6$angle -180, dataset.6$angle)
dataset.6$category <- cut((dataset.6$angle), breaks = seq(0, 360, 15), labels = seq(0, 345, 15))

dataset.6.p <- dcast(setDT(dataset.6), population + bias.class ~ category, length)
dataset.6.p <- reshape2::melt(dataset.6.p, id.vars = c("population", "bias.class"))
colnames(dataset.6.p) <- c("Population", "Bias", "Cluster", "Counts")
dataset.6.p$CountsRatio <- NA

dataset.6.p[dataset.6.p$Population == "LHm" & dataset.6.p$Bias == "Female_biased",]$CountsRatio <- dataset.6.p[dataset.6.p$Population == "LHm" & dataset.6.p$Bias == "Female_biased",]$Counts/sum(dataset.6.p[dataset.6.p$Population == "LHm" & dataset.6.p$Bias == "Female_biased",]$Counts)
dataset.6.p[dataset.6.p$Population == "LHm" & dataset.6.p$Bias == "Male_biased",]$CountsRatio <- dataset.6.p[dataset.6.p$Population == "LHm" & dataset.6.p$Bias == "Male_biased",]$Counts/sum(dataset.6.p[dataset.6.p$Population == "LHm" & dataset.6.p$Bias == "Male_biased",]$Counts)
dataset.6.p[dataset.6.p$Population == "LHm" & dataset.6.p$Bias == "Unbiased",]$CountsRatio <- dataset.6.p[dataset.6.p$Population == "LHm" & dataset.6.p$Bias == "Unbiased",]$Counts/sum(dataset.6.p[dataset.6.p$Population == "LHm" & dataset.6.p$Bias == "Unbiased",]$Counts)

dataset.6.p[dataset.6.p$Population == "Dahomey" & dataset.6.p$Bias == "Female_biased",]$CountsRatio <- dataset.6.p[dataset.6.p$Population == "Dahomey" & dataset.6.p$Bias == "Female_biased",]$Counts/sum(dataset.6.p[dataset.6.p$Population == "Dahomey" & dataset.6.p$Bias == "Female_biased",]$Counts)
dataset.6.p[dataset.6.p$Population == "Dahomey" & dataset.6.p$Bias == "Male_biased",]$CountsRatio <- dataset.6.p[dataset.6.p$Population == "Dahomey" & dataset.6.p$Bias == "Male_biased",]$Counts/sum(dataset.6.p[dataset.6.p$Population == "Dahomey" & dataset.6.p$Bias == "Male_biased",]$Counts)
dataset.6.p[dataset.6.p$Population == "Dahomey" & dataset.6.p$Bias == "Unbiased",]$CountsRatio <- dataset.6.p[dataset.6.p$Population == "Dahomey" & dataset.6.p$Bias == "Unbiased",]$Counts/sum(dataset.6.p[dataset.6.p$Population == "Dahomey" & dataset.6.p$Bias == "Unbiased",]$Counts)

plot.polar <- function(population, bias, y1, y2, y3){

  plot <- ggplot(dataset.6.p[which(dataset.6.p$Population == paste0(population) & dataset.6.p$Bias == paste0(bias)),], 
                 aes(x = Cluster, y = CountsRatio, fill = Bias)) +
  theme_minimal(base_size = 14) +
  geom_bar(stat="identity", width=1, position = "dodge", color="black") +
  ggtitle(paste(population, ifelse(bias == "Female_biased", "FB", "MB"))) +
  #coord_polar(start = 4.58, direction = -1) +
  coord_polar(start = 1.44, direction = -1) +
  theme(axis.text.x = element_blank(),
        axis.text.y = element_blank(),
        panel.grid = element_line(color="#d9d9d9"),
        legend.title = element_blank(),
        legend.position = "none",
        legend.justification = c(0.001, 0.999),
        legend.text = element_text(size = 11),
        legend.background = element_blank(),
        legend.key = element_blank(),
        panel.background = element_rect(size = 0.5, linetype = "solid", color="white"),
        #strip.background = element_rect(fill = "grey"),
        plot.title = element_text(size = 14, hjust = 0.5)) +
    scale_fill_manual(limits=c("Female_biased", "Male_biased", "Unbiased"),
                    labels=c("Female biased", "Male biased", "Unbiased"),
                    values=c("#fb6a4a", "#6baed6", "#cccccc")) +
  geom_text(x=4.1, y=y1, label=paste0(y1), check_overlap = TRUE) +
  geom_text(x=4.1, y=y2, label=paste0(y2), check_overlap = TRUE) +
  geom_text(x=4.1, y=y3, label=paste0(y3), check_overlap = TRUE) +
  xlab(if(bias == "Female_biased"){"log2FC females"}else{"log2FC males"}) +
  ylab(if(bias == "Female_biased"){"log2FC males"}else{"log2FC females"}) +
  theme(axis.title.y = element_text(margin = margin(t = 0, r = -5, b = 0, l = 0))) +
  theme(axis.title.x = element_text(margin = margin(t = -5, r = 0, b = 0, l = 0))) +
  ylim(0, if(population == "LHm"){0.12}else{0.4})
plot
}

plot.lhm.fb <- plot.polar(population = "LHm", bias = "Female_biased", y1=0.06, y2=0.09, y3=0.12)
plot.lhm.mb <- plot.polar(population = "LHm", bias = "Male_biased", y1=0.06, y2=0.09, y3=0.12)
plot.dah.fb <- plot.polar(population = "Dahomey", bias = "Female_biased", y1=0.2, y2=0.3, y3=0.4)
plot.dah.mb <- plot.polar(population = "Dahomey", bias = "Male_biased", y1=0.2, y2=0.3, y3=0.4)

p1 <- ggarrange(plot.lhm.fb, plot.lhm.mb,
               ncol = 2, nrow = 1,  align = "hv", widths = 1, heights = 1, common.legend = F)

p2 <- ggarrange(plot.dah.fb, plot.dah.mb,
               ncol = 2, nrow = 1,  align = "hv", widths = 1, heights = 1, common.legend = F)

p <- ggarrange(p1, p2,
               ncol = 2, nrow = 1)
save_plot("Figures/Polar_Plot.pdf", p, base_width = 10, base_height = 3)
p
```

### Test {.tabset}
#### Test LHm 
```{r, warning=FALSE, message=FALSE, echo=FALSE}
polar.test <- function(population){
  dataset.test <- dataset.6.p[which(dataset.6.p$Population == population),]

  distrib.f2 <- dataset.test[which(dataset.test$Bias == "Female_biased"),]
  distrib.m2 <- dataset.test[which(dataset.test$Bias == "Male_biased"),]

  print("Null hypothesis: the two samples come from the same distribution")
  chisq.test(distrib.f2$Counts, distrib.m2$Counts)
  
}

polar.test(population = "LHm")
```

#### Test Dahomey
```{r, warning=FALSE, message=FALSE, echo=FALSE}
polar.test(population = "Dahomey")
```

# Test changes in specific genes
Contrasts are Old/Young
```{r, warning=FALSE, message=FALSE, echo=FALSE}
list.genes.sdp <- c("FBgn0264270", "FBgn0003741", "FBgn0003449", "FBgn0003977", "FBgn0000662", "FBgn0003742", "FBgn0000504", "FBgn0001276", "FBgn0001185", "FBgn0004652")

list.genes.IIS.TOR <- c("FBgn0044051", "FBgn0036046", "FBgn0044050", "FBgn0044049", "FBgn0044048", "FBgn0044047", "FBgn0044046", "FBgn0036690", "FBgn0013984", "FBgn0001257", "FBgn0024248", "FBgn0015279", "FBgn0015278", "FBgn0020622", "FBgn0026379", "FBgn0020386", "FBgn0260439", "FBgn0010379", "FBgn0023001", "FBgn0038197", "FBgn0003371", "FBgn0020238", "FBgn0004907", "FBgn0264691", "FBgn0029840", "FBgn0013756", "FBgn0032988", "FBgn0261283", "FBgn0262656", "FBgn0261560", "FBgn0260945", "FBgn0015806", "FBgn0261592", "FBgn0020660", "FBgn0086365")

list.genes.IIS.TOR.downstream <- c("FBgn0004852", "FBgn0000261", "FBgn0030506", "FBgn0033127", "FBgn0031461", "FBgn0004507")
```

## Sex determining pathway {.tabset}

### LHm Female
```{r, warning=FALSE, message=FALSE, echo=FALSE}

contrast.calculator.subset <- function(dataset, term1, term2, population, genes){
  dataset$group <- relevel(dataset$group, ref = term2)
  dataset <- nbinomWaldTest(dataset, betaPrior=TRUE)
  set.seed(1)
  res.de <- results(dataset, contrast=c("group", term1, term2))
  res.de <- as.data.frame(res.de)
  res.de <- setDT(res.de, keep.rownames = TRUE)[]
  res.de <- res.de[which(res.de$rn %in% genes),]
  res.de$padj <- p.adjust(res.de$pvalue)
  res.de <- res.de[,c("rn", "log2FoldChange", "padj")]
  colnames(res.de) <- c("Gene", "log2FoldChange", "padj")
  res.de$Population <- paste0(population)
  return(res.de)
}

diffExp.genes.lhm.f <- contrast.calculator.subset(dataset = dds.lhm,
                                term1 = "FemaleA2", term2 = "FemaleA1", 
                                population = "LHm", genes = list.genes.sdp)

diffExp.genes.lhm.f
```

### LHm Male
```{r, warning=FALSE, message=FALSE, echo=FALSE}
diffExp.genes.dah.m <- contrast.calculator.subset(dataset = dds.lhm,
                                term1 = "MaleA2", term2 = "MaleA1", 
                                population = "LHm", genes = list.genes.sdp)

diffExp.genes.dah.m
```

### Dahomey Female
```{r, warning=FALSE, message=FALSE, echo=FALSE}
diffExp.genes.dah.f <- contrast.calculator.subset(dataset = dds.dah,
                                term1 = "FemaleA2", term2 = "FemaleA1", 
                                population = "Dah", genes = list.genes.sdp)

diffExp.genes.dah.f
```

### Dahomey Male
```{r, warning=FALSE, message=FALSE, echo=FALSE}
diffExp.genes.dah.m <- contrast.calculator.subset(dataset = dds.dah,
                                term1 = "MaleA2", term2 = "MaleA1", 
                                population = "Dah", genes = list.genes.sdp)

diffExp.genes.dah.m
```


## IIS/TOR signaling pathways {.tabset}

### LHm Female
```{r, warning=FALSE, message=FALSE, echo=FALSE}
diffExp.genes.lhm.f <- contrast.calculator.subset(dataset = dds.lhm,
                                term1 = "FemaleA2", term2 = "FemaleA1", 
                                population = "LHm", genes = list.genes.IIS.TOR)

diffExp.genes.lhm.f
```

### LHm Male
```{r, warning=FALSE, message=FALSE, echo=FALSE}
diffExp.genes.dah.m <- contrast.calculator.subset(dataset = dds.lhm,
                                term1 = "MaleA2", term2 = "MaleA1", 
                                population = "LHm", genes = list.genes.IIS.TOR)

diffExp.genes.dah.m
```

### Dahomey Female
```{r, warning=FALSE, message=FALSE, echo=FALSE}
diffExp.genes.dah.f <- contrast.calculator.subset(dataset = dds.dah,
                                term1 = "FemaleA2", term2 = "FemaleA1", 
                                population = "Dah", genes = list.genes.IIS.TOR)

diffExp.genes.dah.f
```

### Dahomey Male
```{r, warning=FALSE, message=FALSE, echo=FALSE}
diffExp.genes.dah.m <- contrast.calculator.subset(dataset = dds.dah,
                                term1 = "MaleA2", term2 = "MaleA1", 
                                population = "Dah", genes = list.genes.IIS.TOR)

diffExp.genes.dah.m
```

## downstream of IIS/TOR {.tabset}

### LHm Female
```{r, warning=FALSE, message=FALSE, echo=FALSE}
diffExp.genes.lhm.f <- contrast.calculator.subset(dataset = dds.lhm,
                                term1 = "FemaleA2", term2 = "FemaleA1", 
                                population = "LHm", genes = list.genes.IIS.TOR.downstream)

diffExp.genes.lhm.f
```

### LHm Male
```{r, warning=FALSE, message=FALSE, echo=FALSE}
diffExp.genes.dah.m <- contrast.calculator.subset(dataset = dds.lhm,
                                term1 = "MaleA2", term2 = "MaleA1", 
                                population = "LHm", genes = list.genes.IIS.TOR.downstream)

diffExp.genes.dah.m
```

### Dahomey Female
```{r, warning=FALSE, message=FALSE, echo=FALSE}
diffExp.genes.dah.f <- contrast.calculator.subset(dataset = dds.dah,
                                term1 = "FemaleA2", term2 = "FemaleA1", 
                                population = "Dah", genes = list.genes.IIS.TOR.downstream)

diffExp.genes.dah.f
```

### Dahomey Male
```{r, warning=FALSE, message=FALSE, echo=FALSE}
diffExp.genes.dah.m <- contrast.calculator.subset(dataset = dds.dah,
                                term1 = "MaleA2", term2 = "MaleA1", 
                                population = "Dah", genes = list.genes.IIS.TOR.downstream)

diffExp.genes.dah.m
```

## Fecundity tests

```{r}
# Load Data
AB_Fecundity <- read_delim("../data/fecundity.csv", 
                           ";", escape_double = FALSE, col_types = cols(
                                                                        ID = col_character()), trim_ws = TRUE)

# Subset Data
LHm_dat<-subset(AB_Fecundity,AB_Fecundity$Pop=="LHm")
Dah_dat<-subset(AB_Fecundity,AB_Fecundity$Pop=="Dah")

# Create plots
LHm_dat$SRO<-(LHm_dat$Foc_off/LHm_dat$Foc_Par)/(LHm_dat$Comp_off/LHm_dat$Comp_Par)
Dah_datp<-Dah_dat
Dah_datp$SRO<-(Dah_datp$Foc_off/Dah_datp$Foc_Par)/(Dah_datp$Comp_off/Dah_datp$Comp_Par)

LHMPlot<-ggboxplot(LHm_dat,y="SRO",x="Age", color="Sex",legend.title ="",ylim=c(0,3.5),xlab = "Age (days)")
DAHPlot<-ggboxplot(Dah_datp,y="SRO",x="Age", color="Sex",legend.title ="",ylim=c(0,3.5),xlab = "Age (days)")

AB_boxplots<-ggarrange(LHMPlot,DAHPlot,labels =c( "A","B"),legend = "bottom", common.legend=TRUE)

# Export Figure S1
ggsave("Figures/Suppl1_Fig_AB.pdf",plot=AB_boxplots,device="pdf",width = 16.8, height = 8.4, units = "cm",dpi=1200)

# Modelling the LHm population
model_LHm<-stan_glmer(Foc_off~Sex*as.factor(Age)+offset(log(Foc_Par))+offset(log(Comp_off/Comp_Par)) + (1|ID), family =poisson, 
                      data=LHm_dat,
                      seed=100,
                      cores=8,
                      iter=4000,
                      prior_intercept = normal(location = 0, scale = 10),
                      prior = normal(location = 0, scale = 2.5),
                      warmup=1000)

model_posteriors<-as.data.frame(model_LHm)
mpLHM<-model_posteriors[,1:4]

## Testing if LHm-females have aged
aa<-as.matrix(mpLHM$`as.factor(Age)25`)
Fem<-posterior_interval(aa, prob = 0.95, type = "central", pars = NULL)
FemA<-cbind(Fem,mean(aa))


## Testing if LHm-males have aged
aa<-as.matrix(mpLHM$`as.factor(Age)25`+mpLHM$`SexMale:as.factor(Age)25`)
Mal<-posterior_interval(aa, prob = 0.95, type = "central", pars = NULL)
MalA<-cbind(Mal,mean(aa))

OO<-rbind(FemA,MalA)
rownames(OO)<-c("F_Age","M_Age")
colnames(OO)<-c("2.5%","97.5%","mean")

## Export LHm-results
write.csv2(OO,"Tables/suppl1_LHm.csv")

# Modelling the Dahomey population

## Part to make random draws for Cage_ID for young flies.
Dah_Old<-subset(Dah_dat,Dah_dat$Cage>0)
NO_CAGE<-subset(Dah_dat$Cage,is.na(Dah_dat$Cage))
Young_dah<-subset(Dah_dat,is.na(Dah_dat$Cage))
Dah_dat$Cage<-as.character(Dah_dat$Cage)
Young_dahF<-subset(Young_dah,Young_dah$Sex=="Female")
Young_dahM<-subset(Young_dah,Young_dah$Sex=="Male")

pool<-as.character(c(1,1,1,1,1,1,2,2,2,2,2,2,3,3,3,3,3,3,4,4,4,4,4,4,5,5,5,5,5,5))

randomvials<-as.data.frame(matrix(NA,nrow=length(pool)*2, ncol=100))

for(i in 1:100){
  randomvials[,i]<-sample(pool,size=length(pool),replace = FALSE)
  randomvials[,i]<-sample(pool,size=length(pool),replace = FALSE)
}

names<-c(1:100)
colnames(randomvials)<-names

## Get the actual Cage_ID from the old flies
copyCage<-as.data.frame(matrix(NA,nrow=length(Dah_Old$Cage), ncol=100))
for(i in 1:100){
copyCage[,i]<-Dah_Old$Cage
}

colnames(copyCage)<-names

## Put together the random Cage_IDs (young flies) with the actual Cage_IDs (old flies)
Randy<-rbind(randomvials,copyCage)
Dah_ready<-cbind(Dah_dat,Randy)
Dah_Run<-Dah_ready[,c(2:4,6:9)]


## Set up things for the for-loop and result outputs
TheRun<-Dah_Run
number=100 

outIntercept<-matrix(NA,nrow=12000,ncol=100)
outSexMale<-matrix(NA,nrow=12000,ncol=100)
outAge<-matrix(NA,nrow=12000,ncol=100)
outSexMaleAge<-matrix(NA,nrow=12000,ncol=100)
  
## Run the actual model
for (i in 1:number){
  
  TheRun$Cage<-Dah_ready[,9+i]

  
  rerun_Dah<-stan_glm(Foc_off~Sex*as.factor(Age)+offset(log(Foc_Par))+offset(log(Comp_off/Comp_Par)) + Cage, family =poisson, 
                        data=TheRun,
                        seed=100,
                        cores=4,
                        iter=4000,adapt_delta = 0.95,
                        prior_intercept = normal(location = 0, scale = 10),
                        prior = normal(location = 0, scale = 2.5),
                        warmup=1000)
  
  Dah_re<-as.data.frame(rerun_Dah)
  FF<-(Dah_re[,c(1:3,8)])
  
  outIntercept[,i]<-FF$`(Intercept)`
  outSexMale[,i]<-FF$SexMale
  outAge[,i]<-FF$`as.factor(Age)25`
  outSexMaleAge[,i]<-FF$`SexMale:as.factor(Age)25`
  
}

## Join posterior
FFFF<-outAge #Females
MMMM<-outAge+outSexMaleAge #Males

as_oneF<-as.matrix(c(as.matrix(FFFF)))
as_oneM<-as.matrix(c(as.matrix(MMMM)))

## Testing if females have aged
aa<-as_oneF
Fem<-posterior_interval(aa, prob = 0.95, type = "central", pars = NULL)
FemA<-cbind(Fem,mean(aa))
  
## Testing if males ages
aa<-as_oneM
Mal<-posterior_interval(aa, prob = 0.95, type = "central", pars = NULL)
MalA<-cbind(Mal,mean(aa))
  
DahD<-rbind(FemA,MalA)
rownames(DahD)<-c("F_Age","M_Age")
colnames(DahD)<-c("2.5%","97.5%","mean")

## Export Dahomey results  
write.csv2(DahD,"Tables/suppl1_Dah.csv")
```
## Survival

```{r, warning=FALSE, message=FALSE, echo=FALSE}
df <- read.table(file = "../data/mortality.txt", sep = "\t", header = T)
df2 <- df[,c(1,2,8,9)]
df2 <- melt(df2, id.vars=c("Population", "Replicate"))
colnames(df2) <- c("Population", "Replicate", "Age", "Survival.rate")
df2 <- df2[which(df2$Age=="Survival.Age.2"),]
df2 <- df2[which(df2$Population!="Dah 15x18"),]
```

```{r, warning=FALSE, message=FALSE, echo=FALSE}
summar <- summarySE(df2, measurevar="Survival.rate", groupvars=c("Population"))
summar
```

```{r, warning=FALSE, message=FALSE, echo=FALSE}
model <- lm(Survival.rate ~ Population, data = df2)
Anova(model)
```

```{r, warning=FALSE, message=FALSE, echo=FALSE}
p1 <- ggplot(df2, aes(x = Population, y = Survival.rate, fill = Population)) +
  theme_bw(base_size = 15) +
  geom_boxplot(outlier.colour="black", notch=F, outlier.shape=NA) +
  theme(axis.title.x=element_blank(),
        axis.text.x = element_text(color="black"),
        axis.text.y = element_text(color="black"),
        panel.grid = element_blank())+
  theme(legend.title=element_blank(),
        legend.position = "none",
        legend.justification = c(0.999, 0.999),
        legend.background = element_rect(fill="transparent"),
        legend.key = element_rect(fill="transparent"),
        legend.text = element_text(size = 12),
        panel.background = element_rect(fill = "white",
                                        size = 0.5, linetype = "solid"),
        strip.background = element_rect(fill = "white")) +
  ylim(0,1)
p1

ggsave("Figures/Survival.pdf",plot=p1,device="pdf",width = 10.2, height = 10.2, units = "cm",dpi=1200)
```
